---
title: "Functional_Diversity"
author: "Maggie Klope"
date: "10/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(stats)
library(sjPlot)
library(FD)
library(DHARMa) #model diagnostics
library(glmmTMB) #model fitting
library(MuMIn) #model summaries and comparisons
library(emmeans) #post-hoc analyses
# library(performance) #for R2 values
library(gt)
library(knitr)
library(ggsignif) # for adding significance comparisons to graphs
```

### Calculations

```{r tidy data, include=FALSE}
other_traits <- read_csv("Datasheets/seed_mass_leaf_N.csv")

#making a df just for functional diveristy calculations
for_FD <- read_csv("Datasheets/cwm_traits_updated.csv") %>% 
  left_join(other_traits, by = "species_name") %>% 
  select(climate, treatment, Block, species_name, Abundance, leaf_area, sla, ldmc, seed_mass, leaf_n) %>% 
  drop_na

#abundance data in correct format:
fd_abund <- function(Climate, Treatment){
  as.matrix(for_FD %>% 
    filter(climate == Climate) %>% 
    filter(treatment == Treatment) %>% 
    arrange(species_name) %>% 
    select(Block, species_name, Abundance) %>%
    pivot_wider(names_from = species_name, values_from = Abundance) %>%
    replace(is.na(.), 0) %>% 
    column_to_rownames(var = "Block"))
}

arid_open_abund <- fd_abund("Arid", "Open")
arid_partial_abund <- fd_abund("Arid", "Partial")
arid_total_abund  <- fd_abund("Arid", "Total")

int_open_abund <- fd_abund("Intermediate", "Open")
int_partial_abund <- fd_abund("Intermediate", "Partial")
int_total_abund <- fd_abund("Intermediate", "Total")

mesic_open_abund <- fd_abund("Mesic", "Open")
mesic_partial_abund <- fd_abund("Mesic", "Partial")
mesic_total_abund <- fd_abund("Mesic", "Total")

# trait data in correct format:

fd_traits <- function(Climate, Treatment){
  for_FD %>% 
    # ungroup(climate, treatment) %>% 
    filter(climate == Climate) %>% 
    filter(treatment == Treatment) %>% 
    dplyr::select(species_name, leaf_area, sla, ldmc) %>%
    distinct() %>% 
    arrange(species_name) %>% 
    column_to_rownames(var = "species_name") 
  
}

arid_open_trait <- fd_traits("Arid", "Open")
arid_partial_trait <- fd_traits("Arid", "Partial")
arid_total_trait <- fd_traits("Arid", "Total")

int_open_trait <- fd_traits("Intermediate", "Open")
int_partial_trait <- fd_traits("Intermediate", "Partial")
int_total_trait <- fd_traits("Intermediate", "Total")

mesic_open_trait <- fd_traits("Mesic", "Open")
mesic_partial_trait <- fd_traits("Mesic", "Partial")
mesic_total_trait <- fd_traits("Mesic", "Total")

```

```{r FD calcs, include=FALSE}
arid_open_fd <- dbFD(x = arid_open_trait, a = arid_open_abund)
arid_partial_fd <- dbFD(x = arid_partial_trait, a = arid_partial_abund)
arid_total_fd <- dbFD(x = arid_total_trait, a = arid_total_abund)

int_open_fd <- dbFD(x = int_open_trait, a = int_open_abund)
int_partial_fd <- dbFD(x = int_partial_trait, a = int_partial_abund)
int_total_fd <- dbFD(x = int_total_trait, a = int_total_abund)

mesic_open_fd <- dbFD(x = mesic_open_trait, a = mesic_open_abund)
mesic_partial_fd <- dbFD(x = mesic_partial_trait, a = mesic_partial_abund)
mesic_total_fd <- dbFD(x = mesic_total_trait, a = mesic_total_abund)

FD_arid_open <- as.data.frame(arid_open_fd$FRic) %>% 
  rownames_to_column() %>% 
  rename(FRic = "arid_open_fd$FRic") %>% 
  rename(Block = "rowname") %>% 
  mutate(climate = "Arid") %>% 
  mutate(treatment = "Open") %>% 
  mutate(FEve = arid_open_fd$FEve) %>% 
  mutate(FDiv = arid_open_fd$FDiv) %>% 
  mutate(FDis = arid_open_fd$FDis) %>% 
  mutate(RaoQ = arid_open_fd$RaoQ)
  
FD_arid_partial <- as.data.frame(arid_partial_fd$FRic) %>% 
  rownames_to_column() %>% 
  rename(FRic = "arid_partial_fd$FRic") %>% 
  rename(Block = "rowname") %>% 
  mutate(climate = "Arid") %>% 
  mutate(treatment = "Partial")%>% 
  mutate(FEve = arid_partial_fd$FEve) %>% 
  mutate(FDiv = arid_partial_fd$FDiv) %>% 
  mutate(FDis = arid_partial_fd$FDis) %>% 
  mutate(RaoQ = arid_partial_fd$RaoQ)

FD_arid_total <- as.data.frame(arid_total_fd$FRic) %>% 
  rownames_to_column() %>% 
  rename(FRic = "arid_total_fd$FRic") %>% 
  rename(Block = "rowname") %>% 
  mutate(climate = "Arid") %>% 
  mutate(treatment = "Total")%>% 
  mutate(FEve = arid_total_fd$FEve) %>% 
  mutate(FDiv = arid_total_fd$FDiv) %>% 
  mutate(FDis = arid_total_fd$FDis) %>% 
  mutate(RaoQ = arid_total_fd$RaoQ)

FD_int_open <- as.data.frame(int_open_fd$FRic) %>% 
  rownames_to_column() %>% 
  rename(FRic = "int_open_fd$FRic") %>% 
  rename(Block = "rowname") %>% 
  mutate(climate = "Intermediate") %>% 
  mutate(treatment = "Open")%>% 
  mutate(FEve = int_open_fd$FEve) %>% 
  mutate(FDiv = int_open_fd$FDiv) %>% 
  mutate(FDis = int_open_fd$FDis) %>% 
  mutate(RaoQ = int_open_fd$RaoQ)

FD_int_partial <- as.data.frame(int_partial_fd$FRic) %>% 
  rownames_to_column() %>% 
  rename(FRic = "int_partial_fd$FRic") %>% 
  rename(Block = "rowname") %>% 
  mutate(climate = "Intermediate") %>% 
  mutate(treatment = "Partial")%>% 
  mutate(FEve = int_partial_fd$FEve) %>% 
  mutate(FDiv = int_partial_fd$FDiv) %>% 
  mutate(FDis = int_partial_fd$FDis) %>% 
  mutate(RaoQ = int_partial_fd$RaoQ)

FD_int_total <- as.data.frame(int_total_fd$FRic) %>% 
  rownames_to_column() %>% 
  rename(FRic = "int_total_fd$FRic") %>% 
  rename(Block = "rowname") %>% 
  mutate(climate = "Intermediate") %>% 
  mutate(treatment = "Total")%>% 
  mutate(FEve = int_total_fd$FEve) %>% 
  mutate(FDiv = int_total_fd$FDiv) %>% 
  mutate(FDis = int_total_fd$FDis) %>% 
  mutate(RaoQ = int_total_fd$RaoQ)

FD_mesic_open <- as.data.frame(mesic_open_fd$FRic) %>% 
  rownames_to_column() %>% 
  rename(FRic = "mesic_open_fd$FRic") %>% 
  rename(Block = "rowname") %>% 
  mutate(climate = "Mesic") %>% 
  mutate(treatment = "Open")%>% 
  mutate(FEve = mesic_open_fd$FEve) %>% 
  mutate(FDiv = mesic_open_fd$FDiv) %>% 
  mutate(FDis = mesic_open_fd$FDis) %>% 
  mutate(RaoQ = mesic_open_fd$RaoQ)

FD_mesic_partial <- as.data.frame(mesic_partial_fd$FRic) %>% 
  rownames_to_column() %>% 
  rename(FRic = "mesic_partial_fd$FRic") %>% 
  rename(Block = "rowname") %>% 
  mutate(climate = "Mesic") %>% 
  mutate(treatment = "Partial") %>% 
  mutate(FEve = mesic_partial_fd$FEve) %>% 
  mutate(FDiv = mesic_partial_fd$FDiv) %>% 
  mutate(FDis = mesic_partial_fd$FDis) %>% 
  mutate(RaoQ = mesic_partial_fd$RaoQ)

FD_mesic_total <- as.data.frame(mesic_total_fd$FRic) %>% 
  rownames_to_column() %>% 
  rename(FRic = "mesic_total_fd$FRic") %>% 
  rename(Block = "rowname") %>% 
  mutate(climate = "Mesic") %>% 
  mutate(treatment = "Total")%>% 
  mutate(FEve = mesic_total_fd$FEve) %>% 
  mutate(FDiv = mesic_total_fd$FDiv) %>% 
  mutate(FDis = mesic_total_fd$FDis) %>% 
  mutate(RaoQ = mesic_total_fd$RaoQ)

FD_all <- rbind(FD_arid_open, FD_arid_partial, FD_arid_total, FD_int_open, FD_int_partial, FD_int_total, FD_mesic_open, FD_mesic_partial, FD_mesic_total)
```

```{r}
FD_all %>%
  pivot_longer(cols = c(FRic, FEve:FDis),
               names_to = "FD",
               values_to = "value") %>%
  ggplot(aes(x = climate, y = value, color = treatment)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap(~FD, scales = "free")

# ggsave("Functional_Diversity_Barchart.png", path = "~/github/Tejon_Functional_Traits/Figures")

```

### Graphs

```{r}

# opts_knit$set(root.dir = "~/github/Tejon_Functional_Traits/Villeger_code/functions")

#loading Villeger functions
# setwd("~/github/Tejon_Functional_Traits/Villeger_code/functions") # folder where R functions have been saved

source("quality_funct_space.R")
source("plot_funct_space.R")
source("multidimFD.R")
source("multidimFbetaD.R")

```

```{r,}
# opts_knit$set(root.dir = "~/github/Tejon_Functional_Traits/Figures/FD")

# make sure data is in correct format
sum(row.names(arid_open_trait) %in% colnames(arid_open_abund)) == ncol(arid_open_abund) #TRUE

# first, use quality_funct_space(traits df, plot = "name")
qual_funct_space <- quality_funct_space(arid_open_trait, 
                                        plot = "arid_open_qual_funct_space")

qual_funct_space <- quality_funct_space(as.matrix(arid_open_trait), 
                                        traits_weights = NULL, 
                                        nbdim = 6, 
                                        metric = "Gower",
                                        dendro = TRUE, 
                                        plot = "arid_open_qual_funct_space")

qual_funct_space$meanSD
# best value is the smallest, so in this case 3D

arid_open_coord_3D <- qual_funct_space$details_funct_space$mat_coord[ ,1:3]
arid_open_coord_3D

FD_test <- multidimFD(arid_open_coord_3D, 
                         arid_open_abund, 
                         check_species_pool = TRUE, 
                         verb = TRUE,
                         nm_asb_plot = row.names(arid_open_abund), 
                         folder_plot = "~/github/Tejon_Functional_Traits/Figures/FD",
                         Faxes_plot = colnames(arid_open_coord_3D)[1:3], 
                         Faxes_nm_plot = colnames(arid_open_coord_3D)[1:3],
                         plot_pool = TRUE, 
                         col_bg = "grey90", 
                         col_sp_pool = "grey30",  
                         pch_sp_pool = "+", 
                         cex_sp_pool = 1, 
                         pch_sp = 21, 
                         col_sp = "#1E90FF", 
                         transp = 50)

```

### Models

#### FRic

- averaged over treatment, there is a sig difference between Arid-Int and Int-Mesic, but not Arid-Mesic
- averaged over climate, there is not sig difference between treatments
- Arid
    - Arid Partial > Arid Open
    - Arid Partial > Arid Total
    - No difference between Arid Open and Arid Total
- Int
    - No difference between herbivore treatments at int
- Mesic
  - Mesic Open > Mesic Total
- Open
    - Mesic Open > Arid Open 
    - Mesic Open > Int Open
    - no diff between arid open and int open
- Partial
    - Arid Partial > Intermediate Partial
    - Arid Partial > Mesic Partial
    - No difference between int partial and mesic partial
- Total
    -No difference between climates for total exclosure
    
```{r}
FRic <- glm(data = FD_all, FRic ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(FRic) #best model: FRic ~ climate * treatment

# does data fit model?
simulateResiduals(FRic, plot=T) # looks ok
shapiro.test(residuals(FRic)) # residuals are normal

# significant pairs
FRic_sig_pairs <-  as.data.frame(pairs(emmeans(FRic, ~ climate * treatment)))%>% 
  filter(p.value <= 0.05)

# all pairwise comparisons
emmeans(FRic, pairwise ~ climate)
emmeans(FRic, pairwise ~ treatment)
emmeans(FRic, pairwise ~ climate * treatment)
emmeans(FRic, pairwise ~ climate | treatment)
pairs(emmeans(FRic, ~ climate | treatment)) # same thing


# looking at ggeffects graphs to plot marginal means
library(ggeffects)

dat <- ggpredict(FRic, terms = c("climate", "treatment"))
dat <- ggpredict(FRic, terms = c("treatment", "climate"))
plot(dat, facet = TRUE)
plot(dat)
plot(dat, connect.lines = TRUE, ci.style = "dot")




```

#### FEve

- best fit model is intercept only
- next best model includes climate, but there is no significance
- I checked model fit and data distribution, and it all looked good

```{r}
FEve <- glm(data = FD_all, FEve ~ climate * treatment, family = gaussian, na.action = na.pass)
dredge(FEve) #best model includes only the intercept, going forward with testing for fit to make sure I'm using correct family
FEve <- glm(data = FD_all, FEve ~ 1, family = gaussian, na.action = na.fail)

# does data fit model?
simulateResiduals(FEve, plot=T) # good
shapiro.test(residuals(FEve)) # residuals are normal

ggplot(FD_all, aes(x = FEve)) +
  geom_histogram() +
  theme_bw()

shapiro.test(FD_all$FEve) #data is normal

# next best model:
FEve <- glm(data = FD_all, FEve ~ treatment, family = gaussian, na.action = na.fail)

# does data fit model?
simulateResiduals(FEve, plot=T) # good
shapiro.test(residuals(FEve)) # residuals are normal

# all pairwise comparisons
emmeans(FEve, pairwise ~ treatment) #no significance between treatments

```

#### FDiv

- averaged over climate levels, there is a sig difference between all herbivoretreatments
- averaged over herbivore treatment, there is a sig difference between Arid-Mesic and Int-Mesic
- Arid
    - Arid Open > Arid Partial
    - Arid Total > Arid Open
    - Arid Total > Arid Partial
- Int
    - Int Open > Int Partial
    - Int Total > Int Open
    - Int Total > Int Partial
- Mesic
    - No difference in treatment at mesic
- Open
    - No difference between climates for open treatments
- Partial
    - Mesic Partial > Arid Partial
    - Mesic Partial > Int Partial
    - No difference in int partial and arid partial
-Total
    - No difference between climates for total exclosure

```{r}
FDiv <- glm(data = FD_all, FDiv ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(FDiv) #best model: FDiv ~ climate * treatment

# does data fit model?
simulateResiduals(FDiv, plot=T) # looks ok
shapiro.test(residuals(FDiv)) # residuals are  normal

# significant pairs
FDiv_sig_pairs <-  as.data.frame(pairs(emmeans(FDiv, ~ climate * treatment)))%>% 
  filter(p.value <= 0.05)

# all pairwise comparisons
emmeans(FDiv, pairwise ~ climate)
emmeans(FDiv, pairwise ~ treatment)
# emmeans(FDiv, pairwise ~ climate * treatment)
emmeans(FDiv, pairwise ~ climate | treatment)
```

#### FDis

- Averaged over treatment, sig difference between Arid-Mesic and Int-Mesic
- Averaged over climate, sig difference between Open-Partial and Open-Total, but not Open-Partial
- Arid
    - Arid Total > Arid Open
    - Arid Total > Arid Partial
    - No difference between Open and Partial
- Int
    - Int Total > Int Open
    - Int Total > Int Partial
    - No difference between Open and Partial
- Mesic
    - Mesic Open > Mesic Partial
    - No dif between Total-Open
    - No dif between Total-Partial
- Open
    - Mesic Open > Arid Open
    - Mesic Open > Int Open
    - No differecne for Arid-Int
- Partial
    - Mesic Partial > Arid Partial
    - Mesic Partial > Int Partial
      - No differecne for Arid-Int
- Total
    - Int Total > Arid Total
    - Int Total > Mesic Total
    - No difference between Mesic-Arid
    
```{r}
FDis <- glm(data = FD_all, FDis ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(FDis) #best model: FDis ~ climate * treatment

# does data fit model?
simulateResiduals(FDis, plot=T) # looks ok
shapiro.test(residuals(FDis)) # residuals are normal

# significant pairs
FDis_sig_pairs <-  as.data.frame(pairs(emmeans(FDis, ~ climate * treatment)))%>% 
  filter(p.value <= 0.05)

# all pairwise comparisons
emmeans(FDis, pairwise ~ climate)
emmeans(FDis, pairwise ~ treatment)
# emmeans(FDis, pairwise ~ climate * treatment)
emmeans(FDis, pairwise ~ climate | treatment)

```

#### RaoQ

```{r RaoQ, include=FALSE}
RaoQ <- glmmTMB(data = FD_all, RaoQ ~ climate * treatment, family = gaussian)
dredge(RaoQ) #best model: RaoQ ~ climate * treatment

# does data fit model?
simulateResiduals(RaoQ, plot=T) # Looks like there is a weird pattern
shapiro.test(residuals(RaoQ)) # but residuals are normal

#significant pairs
RaoQ_sig_pairs <-  as.data.frame(pairs(emmeans(RaoQ, ~ climate * treatment)))%>% 
  filter(p.value <= 0.05)

#all pairs
emmeans(RaoQ, pairwise ~ climate * treatment)

```

#### Best-Fit & AIC Table

```{r}

dredge_FRic <- as.data.frame(dredge(FRic)) %>%
  filter(AICc == min(AICc)) %>% 
  mutate(CWM = "FRic") %>% 
  dplyr::select(CWM, climate, treatment, "climate:treatment")

dredge_FEve <- as.data.frame(dredge(FEve)) %>%
  filter(AICc == min(AICc)) %>% 
  mutate(CWM = "FEve") %>%
  dplyr::select(CWM)

dredge_FDiv <- as.data.frame(dredge(FDiv)) %>%
  filter(AICc == min(AICc)) %>% 
  mutate(CWM = "FDiv") %>%
  dplyr::select(CWM, climate, treatment, "climate:treatment")

dredge_FDis <- as.data.frame(dredge(FDis)) %>%
  filter(AICc == min(AICc)) %>% 
  mutate(CWM = "FDis") %>%
  dplyr::select(CWM, climate, treatment, "climate:treatment")

dredge_table <- dredge_FRic %>% 
  full_join(dredge_FEve) %>% 
  full_join(dredge_FDiv) %>% 
  full_join(dredge_FDis) %>% 
  mutate(climate = str_replace(climate, "\\+","x")) %>%
  mutate(treatment = str_replace(treatment, "\\+","x")) %>% 
  mutate(`climate:treatment` = str_replace(`climate:treatment`, "\\+","x"))

pretty_table <- dredge_table %>% 
  as_tibble() %>% 
  gt() %>% 
  tab_header(
    title = "FD Best-Fit Models"
  ) %>% 
  tab_spanner(
    label = "Fixed Effects Terms",
    columns = vars(climate, treatment, "climate:treatment")
  ) %>% 
  # fmt_number(
  #   columns = vars(AICc),
  #   decimals = 2
  # ) %>% 
  fmt_missing(
    columns = vars(climate, treatment, "climate:treatment"),
    missing_text = " "
  ) %>% 
  tab_source_note(
    source_note = "x indicates selection of fixed effect term for best-fit model"
  )

pretty_table

# gtsave(data = pretty_table, filename = "FD_Best_Fit_table.png", path = "~/github/Tejon_Functional_Traits/Figures")

```
#### EMM Graphs
```{r}
# color of arrows
arrow_colors <- (rep(c("red", "orange", "blue"), 3))

# significance caption
symbol <- "\u2264"
caption <- paste0(symbol, "0.05(*), ", symbol, "0.01()**, ", symbol, "0.001(***)")

emm_plot <- function(emmeans) {
  plot(emmeans, by = NULL, CIs = FALSE, comparisons = TRUE, horizontal = FALSE, colors = "darkgreen") +
  # facet_grid by climate, and remove empty values
  # facet_grid(. ~climate, scales = "free", space = "free") +
  labs(y = "EMM", x = "Climate") +
  aes(fill = as.factor(treatment)) +
  # changing color of comparison arrow lines
  geom_segment(aes_(y = ~the.emmean, yend = ~lcmpl, x = ~pri.fac, xend = ~pri.fac), #copied from function's code on github
               arrow = arrow(length = ggplot2::unit(.07, "inches"), type = "closed"),
               color = arrow_colors) +
  geom_segment(ggplot2::aes_(y = ~the.emmean, yend = ~rcmpl, x = ~pri.fac, xend = ~pri.fac),
               arrow = arrow(length = ggplot2::unit(.07, "inches"), type = "closed"),
               color = arrow_colors) +
  # changing color of point
  geom_point(aes_(fill = "black")) +
  # changing theme
  theme_bw() +
  # removing legend
  theme(legend.position = "none") +
  # changing x labels within facet_grid
  scale_x_discrete(labels = c("Open", "Partial", "Total", "Open", "Partial", "Total", "Open", "Partial", "Total")) +
  # transparent background
  theme(panel.background = element_rect(fill = "transparent"), plot.background = element_rect(fill = "transparent", color = NA)) +
  # adding footnote
  labs(caption = caption)
}

# FRic
FRic_emmeans <- emmeans(FRic, ~ treatment | climate)
# emmeans(FRic, pairwise ~ treatment | climate)
FRic_plot <- emm_plot(FRic_emmeans) +
  labs(title = "Functional Richness") +
  # Arid-Open - Arid-Partial
  geom_signif(annotation = "***",
    y_position = 7.25, xmin = 1, xmax = 2,
    tip_length = c(.7, .025)) +
  # Arid-Partial - Arid-Total
  geom_signif(annotation = "**",
    y_position = 7.75, xmin = 2, xmax = 3,
    tip_length = c(.05, .5)) +
  # Mesic-Open - Mesic-Partial
   geom_signif(annotation = "*",
    y_position = 7.2, xmin = 7, xmax = 8,
    tip_length = c(.05, .3)) +
    # Mesic-Open - Mesic-Total
   geom_signif(annotation = "**",
    y_position = 5, xmin = 8, xmax = 9,
    tip_length = c(.05, .2))

ggsave("FRic_emmean.png", plot = FRic_plot, path = "~/github/Tejon_Functional_Traits/Figures", height = 4, width = 5, bg = "transparent")

# FDiv
FDiv_emmeans <- emmeans(FDiv, ~ treatment | climate)
# emmeans(FDiv, pairwise ~ treatment | climate)
FDiv_plot <- emm_plot(FDiv_emmeans) +
  labs(title = "Functional Divergence") +
  # Arid-Open - Arid-Partial
  geom_signif(annotation = "***",
    y_position = .8, xmin = 1, xmax = 2,
    tip_length = c(.05, .5)) +
  # Arid-Open - Arid-Total
  geom_signif(annotation = "*",
    y_position = 1.05, xmin = 1, xmax = 3,
    tip_length = c(.4, .1)) +
  # Arid-Partial - Arid-Total
  geom_signif(annotation = "***",
    y_position = .95, xmin = 2, xmax = 3,
    tip_length = c(.05, .05)) +
  # Int all
  geom_signif(annotation = "***",
    y_position = .8, xmin = 4, xmax = 5,
    tip_length = c(.05, .5)) +
  geom_signif(annotation = "***",
    y_position = .95, xmin = 5, xmax = 6,
    tip_length = c(.05, .05)) +
  geom_signif(annotation = "***",
    y_position = 1.05, xmin = 4, xmax = 6,
    tip_length = c(.4, .1)) +
  # Mesic-Partial - Mesic-Total
  geom_signif(annotation = "*",
    y_position = .9, xmin = 8, xmax = 9,
    tip_length = c(.3, .05))

ggsave("FDiv_emmean.png", plot = FDiv_plot, path = "~/github/Tejon_Functional_Traits/Figures", height = 4, width = 5, bg = "transparent")

# FDis
FDis_emmeans <- emmeans(FDis, ~ treatment | climate)
# emmeans(FDis, pairwise ~ treatment | climate)
FDis_plot <- emm_plot(FDis_emmeans) +
  labs(title = "Functional Dispersion") +
  # Arid-Open - Arid-Total
  geom_signif(annotation = "***",
    y_position = 1.5, xmin = 1, xmax = 3,
    tip_length = c(.5, .05)) +
    # Arid-Partial - Arid-Total
  geom_signif(annotation = "**",
    y_position = 1.4, xmin = 2, xmax = 3,
    tip_length = c(.3, .05)) +
  # Int-Open - Int-Total
   geom_signif(annotation = "***",
    y_position = 1.9, xmin = 4, xmax = 6,
    tip_length = c(.85, .05)) +
  # Int-Partial - Int-Total
   geom_signif(annotation = "***",
    y_position = 1.8, xmin = 5, xmax = 6,
    tip_length = c(.8, .05)) +
  # Mesic-Open - Mesic-Partial
  geom_signif(annotation = "**",
    y_position = 1.7, xmin = 7, xmax = 8,
    tip_length = c(.05, .3)) +
  # Mesic-Open - Mesic-Total
  geom_signif(annotation = "*",
    y_position = 1.8, xmin = 7, xmax = 9,
    tip_length = c(.05, .35))

ggsave("FDis_emmean.png", plot = FDis_plot, path = "~/github/Tejon_Functional_Traits/Figures", height = 4, width = 5, bg = "transparent")

```

