---
title: "Functional_Group_Models"
author: "Maggie Klope"
date: "1/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(stats)
library(sjPlot)
library(FD)
library(DHARMa) #model diagnostics
library(glmmTMB) #model fitting
library(MuMIn) #model summaries and comparisons
library(emmeans) #post-hoc analyses
library(gt)
library(tibble)
library(lsmeans)
library(gridExtra)
library(multcomp)
library(car)

other_traits <- read_csv("Datasheets/seed_mass_leaf_N.csv")

cwm_traits_adj <-  read_csv("Datasheets/cwm_traits_updated.csv") %>% 
  left_join(other_traits, by = "species_name") %>% 
  mutate(weighted_la = leaf_area * Abundance) %>% #multiplying trait values by species abundance
  mutate(weighted_sla = sla * Abundance) %>% 
  mutate(weighted_ldmc = ldmc * Abundance) %>%
  mutate(weighted_seed_mass = seed_mass * Abundance) %>%
  mutate(weighted_n = leaf_n * Abundance) %>%
  group_by(climate, treatment, Block) %>% #grouping by climate, treatment, and block
  summarise_all(mean, na.rm = TRUE) %>% #finding the mean
  dplyr::select(climate, treatment, Block, weighted_la, weighted_sla, weighted_ldmc, weighted_seed_mass, weighted_n)

# log transformation for seed mass & leaf n
cwm_traits_adj <- cwm_traits_adj %>% 
  mutate(log_seed_mass = log(weighted_seed_mass)) %>% 
  mutate(log_n = log(weighted_n))

```

```{r}
cwm_functional <-  read_csv("~/github/Tejon_Functional_Traits/Datasheets/cwm_traits_updated.csv") %>%
  left_join(other_traits, by = "species_name") %>% 
  mutate(weighted_la = leaf_area * Abundance) %>% #multiplying trait values by species abundance
  mutate(weighted_sla = sla * Abundance) %>% 
  mutate(weighted_ldmc = ldmc * Abundance) %>%
  mutate(weighted_seed_mass = seed_mass * Abundance) %>%
  mutate(weighted_n = leaf_n * Abundance) %>%
  group_by(climate, treatment, Block, functional_group) %>% #grouping by climate, treatment, and block
  summarise_all(mean, na.rm = TRUE) %>% #finding the mean
  dplyr::select(climate, treatment, functional_group, weighted_la, weighted_sla, weighted_ldmc, weighted_seed_mass, weighted_n)

cwm_functional %>%
  pivot_longer(cols = weighted_la:weighted_n,
               names_to = "traits",
               values_to = "value") %>%
  ggplot(aes(x = climate, y = value, color = treatment)) +
  geom_boxplot() +
  theme_bw() +
  facet_grid(traits ~ functional_group, scales = "free")

grass <- cwm_functional %>% 
  filter(functional_group == "grass")

forb <- cwm_functional %>% 
  filter(functional_group == "forb") %>% 
  mutate(sqrt_la = sqrt(weighted_la))

shrub <- cwm_functional %>% 
  filter(functional_group == "shrub")
  
```

#### CWMs with interaction between climate, treatment, and functional group

##### leaf area
```{r}
#leaf area is very skewed:
ggplot(cwm_functional, aes(x = weighted_la)) +
  geom_histogram() +
  theme_bw()+
  facet_wrap(~functional_group)

#trying glm
funct_la <- glm(data = cwm_functional, weighted_la ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
dredge(funct_la)

simulateResiduals(funct_la, plot= T) #does not pass dispersion test
shapiro.test(residuals(funct_la)) #but residuals are normal

testDispersion(simulateResiduals(funct_la, plot= T)) # does not pass

#trying log transformation with gaussian
cwm_functional <- cwm_functional %>% 
  mutate(log_la = log(weighted_la))

ggplot(cwm_functional, aes(x = log_la)) +
  geom_histogram() +
  theme_bw()+
  facet_wrap(~functional_group)

funct_la <- glm(data = cwm_functional, log_la ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
dredge(funct_la)
funct_la <- glm(data = cwm_functional, log_la ~ climate + treatment + functional_group + climate:functional_group + functional_group:treatment, family = gaussian, na.action = na.fail)

simulateResiduals(funct_la, plot= T) #looks good
shapiro.test(residuals(funct_la)) # but residuals are not normal

# trying Gamma with log link on un-transformed
funct_la <- glm(data = cwm_functional, weighted_la ~ climate * treatment * functional_group, family = Gamma(link = "log"), na.action = na.fail)
dredge(funct_la)
funct_la <- glm(data = cwm_functional, weighted_la ~ climate + treatment + functional_group + climate:functional_group + functional_group:treatment, family = Gamma(link = "log"), na.action = na.fail)

simulateResiduals(funct_la, plot= T) #does not pass dispersion test, but is very close!
shapiro.test(residuals(funct_la)) #but residuals are normal

#trying log+1 with gaussian
cwm_functional <- cwm_functional %>% 
  mutate(log_plus_la = log(weighted_la + 1))

ggplot(cwm_functional, aes(x = log_plus_la)) +
  geom_histogram() +
  theme_bw()

funct_la <- glm(data = cwm_functional, log_plus_la ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
dredge(funct_la)
funct_la <- glm(data = cwm_functional, log_plus_la ~ climate + treatment + functional_group + climate:functional_group + functional_group:treatment, family = gaussian, na.action = na.fail)

simulateResiduals(funct_la, plot= T) #good
shapiro.test(residuals(funct_la)) #residuals are normal

emmeans(funct_la, pairwise ~ climate | treatment | functional_group)
emmeans(funct_la, pairwise ~ treatment | functional_group)
emmeans(funct_la, pairwise ~ climate | functional_group)
emmeans(funct_la, pairwise ~ functional_group)

# LA_funct_sig_pairs <- as.data.frame(pairs(emmeans(funct_la, ~ climate * treatment * functional_group))) %>% 
#   separate(contrast, c("A", "B"), sep = " - ") %>% 
#   separate(A, c("A_climate", "A_treatment", "A_functional_group"), sep = ",") %>% 
#   separate(B, c("B_climate", "B_treatment", "B_functional_group"), sep = ",") %>% 
#   filter((A_climate == B_climate & A_functional_group == B_functional_group) | 
#           (A_climate == B_climate & A_treatment == B_treatment) | 
#            (A_treatment == B_treatment & A_functional_group == B_functional_group))
# LA_funct_sig_pairs

```
##### specific leaf area
```{r}
#leaf area is very skewed:
ggplot(cwm_functional, aes(x = weighted_sla)) +
  geom_histogram() +
  theme_bw()+
  facet_wrap(~functional_group)

cwm_functional <- cwm_functional %>% 
  mutate(log_sla = log(weighted_sla))

funct_sla <- glm(data = cwm_functional, weighted_sla ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
dredge(funct_sla)

simulateResiduals(funct_sla, plot= T) #does not pass dispersion test
shapiro.test(residuals(funct_sla)) # not normal

#trying log transformation with gaussian
funct_sla <- glm(data = cwm_functional, log_sla ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
dredge(funct_sla)
funct_sla <- glm(data = cwm_functional, log_sla ~ climate + functional_group + treatment + climate:functional_group, family = gaussian, na.action = na.fail)

simulateResiduals(funct_sla, plot= T) # good
shapiro.test(residuals(funct_sla)) # not normal

# trying Gamma with log link on un-transformed
funct_sla <- glm(data = cwm_functional, weighted_sla ~ climate * treatment * functional_group, family = Gamma, na.action = na.fail)
dredge(funct_sla)
funct_sla <- glm(data = cwm_functional, weighted_sla ~ climate + functional_group + treatment + climate:functional_group, family = Gamma, na.action = na.fail)

simulateResiduals(funct_sla, plot= T) # not normal
shapiro.test(residuals(funct_sla)) # not normal

#trying log+1 with gaussian
cwm_functional <- cwm_functional %>% 
  mutate(log_plus_sla = log(weighted_sla + 1))

funct_sla <- glm(data = cwm_functional, log_plus_sla ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
dredge(funct_sla)
funct_sla <- glm(data = cwm_functional, log_plus_sla ~ climate + functional_group + treatment + climate:functional_group, family = gaussian, na.action = na.fail)

simulateResiduals(funct_sla, plot= T) #good
shapiro.test(residuals(funct_sla)) #normal

emmeans(funct_sla, pairwise ~ climate | treatment | functional_group)
emmeans(funct_sla, pairwise ~ treatment | functional_group)
emmeans(funct_sla, pairwise ~ functional_group)

```
##### ldmc
```{r}
cwm_functional <- cwm_functional %>% 
  mutate(log_ldmc = log(weighted_ldmc))

funct_ldmc <- glm(data = cwm_functional, weighted_ldmc ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
dredge(funct_ldmc)
funct_ldmc <- glm(data = cwm_functional, weighted_ldmc ~ climate + functional_group + treatment + climate:functional_group + functional_group:treatment, na.action = na.fail)

simulateResiduals(funct_ldmc, plot= T) # does not pass dispersion test
shapiro.test(residuals(funct_ldmc)) # not normal

funct_ldmc <- glm(data = cwm_functional, log_ldmc ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
dredge(funct_ldmc)
funct_ldmc <- glm(data = cwm_functional, log_ldmc ~ climate + functional_group + treatment + climate:functional_group + functional_group:treatment, na.action = na.fail)

simulateResiduals(funct_ldmc, plot= T) # ok
shapiro.test(residuals(funct_ldmc)) # normal

emmeans(funct_ldmc, pairwise ~ climate | treatment | functional_group)
emmeans(funct_ldmc, pairwise ~ treatment | functional_group)
emmeans(funct_ldmc, pairwise ~ functional_group)
```
##### lnc
```{r}
funct_n <- glm(data = cwm_functional, weighted_n ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
dredge(funct_n)
funct_n <- glm(data = cwm_functional, weighted_n ~ climate + functional_group + treatment + climate:functional_group + functional_group:treatment, na.action = na.fail)

simulateResiduals(funct_n, plot= T) # not good
shapiro.test(residuals(funct_n)) # not normal

cwm_functional <- cwm_functional %>% 
  mutate(log_n = log(weighted_n)) %>% 
  mutate(log_plus_n = log(weighted_n+1))

# trying log transformation with gaussian
funct_n <- glm(data = cwm_functional, log_n ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
dredge(funct_n)
funct_n <- glm(data = cwm_functional, log_n ~ climate + functional_group + treatment + climate:functional_group, na.action = na.fail)

simulateResiduals(funct_n, plot= T) # looks ok
shapiro.test(residuals(funct_n)) # not normal

# trying log(n+1) transformation with gaussian
funct_n <- glm(data = cwm_functional, log_plus_n ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
dredge(funct_n)
funct_n <- glm(data = cwm_functional, log_plus_n ~ climate + functional_group + treatment + climate:functional_group, na.action = na.fail)

simulateResiduals(funct_n, plot= T) # looks ok
shapiro.test(residuals(funct_n)) # normal

emmeans(funct_n, pairwise ~ climate | treatment | functional_group)
emmeans(funct_n, pairwise ~ treatment | functional_group)
emmeans(funct_n, pairwise ~ functional_group)

```
##### seed mass
```{r}
funct_seed_mass <- glm(data = cwm_functional, weighted_seed_mass ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
dredge(funct_seed_mass)
funct_seed_mass <- glm(data = cwm_functional, weighted_seed_mass ~ climate + functional_group + treatment + climate:functional_group, na.action = na.fail)

simulateResiduals(funct_seed_mass, plot= T) # bad
shapiro.test(residuals(funct_seed_mass)) # not normal

# log transformation with gaussian
cwm_functional <- cwm_functional %>% 
  mutate(log_seed_mass = log(weighted_seed_mass))

funct_seed_mass <- glm(data = cwm_functional, log_seed_mass ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
dredge(funct_seed_mass)
funct_seed_mass <- glm(data = cwm_functional,log_seed_mass ~ climate + functional_group + climate:functional_group, na.action = na.fail)

simulateResiduals(funct_seed_mass, plot= T) # ok
shapiro.test(residuals(funct_seed_mass)) # normal

# for back transformation
funct_seed_mass <- glm(data = cwm_functional, log(weighted_seed_mass) ~ climate + functional_group + climate:functional_group, na.action = na.fail)

funct_seed_mass_emm <- emmeans(funct_seed_mass, ~ climate * functional_group)
summary(funct_seed_mass_emm) # results are given on a log scale
summary(funct_seed_mass_emm, infer = TRUE, null = log(35), type = "response")

funct_seed_mass.rg <- update(ref_grid(funct_seed_mass), tran = make.tran("genlog", 1))

contrast(regrid(funct_seed_mass.rg))

emmeans(funct_seed_mass.rg, pairwise ~ climate | functional_group)
emmeans(funct_seed_mass, pairwise ~ climate | functional_group)
emmeans(funct_seed_mass, pairwise ~ climate | functional_group)
emmeans(funct_seed_mass, pairwise ~ functional_group)

```
#### Individual Models:
#### a. grasses:
##### i. leaf area
```{r}
grass_la <- glm(data = grass, weighted_la ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(grass_la) # best model: trait ~ climate * treatment

simulateResiduals(grass_la, plot= T) #good
shapiro.test(residuals(grass_la)) #normal

summary(grass_la)
emmeans(grass_la, pairwise ~ climate)
emmeans(grass_la, pairwise ~ treatment | climate)
```
##### ii. specific leaf area
```{r}
grass_sla <- glm(data = grass, weighted_sla ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(grass_sla) # best model: trait ~ climate * treatment

simulateResiduals(grass_sla, plot= T) # good
shapiro.test(residuals(grass_sla)) # normal

summary(grass_sla)
emmeans(grass_sla, pairwise ~ climate)
emmeans(grass_sla, pairwise ~ treatment | climate)
```
##### iii.ldmc
```{r}
grass_ldmc <- glm(data = grass, weighted_ldmc ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(grass_ldmc) # best model: trait ~ climate + treatment
grass_ldmc <- glm(data = grass, weighted_ldmc ~ climate + treatment, family = gaussian, na.action = na.fail)

simulateResiduals(grass_ldmc, plot= T) # not good
shapiro.test(residuals(grass_ldmc)) # not normal

grass <- grass %>% 
  mutate(log_ldmc = log(weighted_ldmc))

grass_ldmc <- glm(data = grass, log_ldmc ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(grass_ldmc) # best model: trait ~ climate
grass_ldmc <- glm(data = grass, log_ldmc ~ climate, family = gaussian, na.action = na.fail)

simulateResiduals(grass_ldmc, plot= T) # good
shapiro.test(residuals(grass_ldmc)) # normal

summary(grass_ldmc)
emmeans(grass_ldmc, pairwise ~ climate)
```
##### iv. lnc
```{r}
grass_n <- glm(data = grass, weighted_n ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(grass_n) # best model: trait ~ climate
grass_n <- glm(data = grass, weighted_n ~ climate, family = gaussian, na.action = na.fail)

simulateResiduals(grass_n, plot= T) # good
shapiro.test(residuals(grass_n)) # normal

summary(grass_n)
emmeans(grass_n, pairwise ~ climate)
```
##### v. seed mass
```{r}
grass_seed_mass <- glm(data = grass, weighted_seed_mass ~ climate * treatment, family = gaussian, na.action = na.fail)
boxcox(grass_seed_mass) # might be best to do ln transformation
dredge(grass_seed_mass) # best model: trait ~ climate + treatment
grass_seed_mass <- glm(data = grass, weighted_seed_mass ~ climate + treatment, family = gaussian, na.action = na.fail)

simulateResiduals(grass_seed_mass, plot= T) # not good
shapiro.test(residuals(grass_seed_mass)) # normal

grass <- grass %>% 
  mutate(log_seed_mass = log(weighted_seed_mass)) %>% 
  mutate(ln_seed_mass = log10(weighted_seed_mass)) %>% 
  mutate(sqrt_seed_mass = sqrt(weighted_seed_mass))

grass_seed_mass <- glm(data = grass, log_seed_mass ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(grass_seed_mass) # best model: trait ~ climate
grass_seed_mass <- glm(data = grass, log_seed_mass ~ climate, family = gaussian, na.action = na.fail)

simulateResiduals(grass_seed_mass, plot= T) # ok?
shapiro.test(residuals(grass_seed_mass)) # not normal

grass_seed_mass <- glm(data = grass, ln_seed_mass ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(grass_seed_mass) # best model: trait ~ climate
grass_seed_mass <- glm(data = grass, ln_seed_mass ~ climate, family = gaussian, na.action = na.fail)

simulateResiduals(grass_seed_mass, plot= T) # ok?
shapiro.test(residuals(grass_seed_mass)) # not normal

grass_seed_mass <- glm(data = grass, sqrt_seed_mass ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(grass_seed_mass) # best model: trait ~ climate + treatment
grass_seed_mass <- glm(data = grass, sqrt_seed_mass ~ climate + treatment, family = gaussian, na.action = na.fail)

simulateResiduals(grass_seed_mass, plot= T) # not ok
shapiro.test(residuals(grass_seed_mass)) # normal

# gamma distribution worked all along
grass_seed_mass <- glm(data = grass, weighted_seed_mass ~ climate * treatment, family = Gamma, na.action = na.fail)
dredge(grass_seed_mass) # best model: trait ~ climate + treatment
grass_seed_mass <- glm(data = grass, weighted_seed_mass ~ climate + treatment, family = Gamma, na.action = na.fail)

simulateResiduals(grass_seed_mass, plot= T) # good
shapiro.test(residuals(grass_seed_mass)) # normal

summary(grass_seed_mass)
emmeans(grass_seed_mass, pairwise ~ climate)
emmeans(grass_seed_mass, pairwise ~ treatment | climate)
```
#### b. forbs
##### i. la
```{r}
forb_la <- glm(data = forb, log_la ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(forb_la) # best model is climate + treatment
forb_la <- glm(data = forb, log_la ~ climate + treatment, family = gaussian, na.action = na.fail)

simulateResiduals(forb_la, plot= T) # ok
shapiro.test(residuals(forb_la)) #normal

summary(forb_la)
emmeans(forb_la, pairwise ~ climate)
emmeans(forb_la, pairwise ~ treatment | climate)
```
##### ii. sla
```{r}
forb_sla <- glm(data = forb, weighted_sla ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(forb_sla) # best model is only climate
forb_sla <- glm(data = forb, weighted_sla ~ climate, family = gaussian, na.action = na.fail)

simulateResiduals(forb_sla, plot= T) # ok
shapiro.test(residuals(forb_sla)) # not normal

forb_sla <- glm(data = forb, weighted_sla ~ climate * treatment, family = Gamma, na.action = na.fail)
dredge(forb_sla) # best model: trait ~ climate
forb_sla <- glm(data = forb, weighted_sla ~ climate, family = Gamma, na.action = na.fail)

simulateResiduals(forb_sla, plot= T) # ok
shapiro.test(residuals(forb_sla)) # normal

summary(forb_sla)
emmeans(forb_sla, pairwise ~ climate)
```
##### iii. ldmc
```{r}
forb_ldmc <- glm(data = forb, weighted_ldmc ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(forb_ldmc) # best model: trait ~ treatment
forb_ldmc <- glm(data = forb, weighted_ldmc ~ treatment, family = gaussian, na.action = na.fail)

simulateResiduals(forb_ldmc, plot= T) # ok
shapiro.test(residuals(forb_ldmc)) # normal

summary(forb_ldmc)
emmeans(forb_ldmc, pairwise ~ treatment)
```
##### iv.lnc
```{r}
forb_leaf_n <- glm(data = forb, weighted_n ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(forb_leaf_n) # best model: trait ~ climate
forb_leaf_n <- glm(data = forb, weighted_n ~ climate, family = gaussian, na.action = na.fail)

simulateResiduals(forb_leaf_n, plot= T) # ok
shapiro.test(residuals(forb_leaf_n)) # normal

summary(forb_leaf_n)
emmeans(forb_leaf_n, pairwise ~ climate)
```
##### v.seed mass
```{r}
forb_seed_mass <- glm(data = forb, weighted_seed_mass ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(forb_seed_mass) # best model: trait ~ climate * treatment

simulateResiduals(forb_seed_mass, plot= T) # not good
shapiro.test(residuals(forb_seed_mass)) # not normal

forb_seed_mass <- glm(data = forb, weighted_seed_mass ~ climate * treatment, family = Gamma, na.action = na.fail)
dredge(forb_seed_mass) # best model: trait ~ climate * treatment

simulateResiduals(forb_seed_mass, plot= T) # ok
shapiro.test(residuals(forb_seed_mass)) # not normal

forb <- forb %>% 
  mutate(log_seed_mass = log(weighted_seed_mass))

forb_seed_mass <- glm(data = forb, log_seed_mass ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(forb_seed_mass) # best model: trait ~ climate
forb_seed_mass <- glm(data = forb, log_seed_mass ~ climate, family = gaussian, na.action = na.fail)

simulateResiduals(forb_seed_mass, plot= T) # ok
shapiro.test(residuals(forb_seed_mass)) # normal

summary(forb_seed_mass)
emmeans(forb_seed_mass, pairwise ~ climate)
```
#### c. shrubs
##### i.la
- what do you do when residuals are normal but the residual vs. predicted plot looks terrible?
```{r}
shrub_la <- glm(data = shrub, weighted_la ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(shrub_la) # best model: trait ~ climate + treatment
shrub_la  <- glm(data = shrub, weighted_la ~ climate + treatment, family = gaussian, na.action = na.fail)

simulateResiduals(shrub_la, plot= T) # very bad
shapiro.test(residuals(shrub_la)) # normal

summary(shrub_la)
emmeans(shrub_la, pairwise ~ climate)
```
##### ii.sla
```{r}
shrub_sla <- glm(data = shrub, weighted_sla ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(shrub_sla) # best model: trait ~ 1
shrub_sla  <- glm(data = shrub, weighted_sla ~ 1, family = gaussian, na.action = na.fail)

simulateResiduals(shrub_sla, plot= T) # fine
shapiro.test(residuals(shrub_sla)) # normal

```
##### iii.ldmc
```{r}
shrub_ldmc <- glm(data = shrub, weighted_ldmc ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(shrub_ldmc) # best model: trait ~ treatment; NEED TO DO MODEL AVERAGING
shrub_ldmc  <- glm(data = shrub, weighted_ldmc ~ treatment, family = gaussian, na.action = na.fail)

simulateResiduals(shrub_ldmc, plot= T) # fine
shapiro.test(residuals(shrub_ldmc)) # normal

summary(shrub_ldmc)
emmeans(shrub_ldmc, pairwise ~ treatment)
```
##### iv.lnc
```{r}
shrub_n <- glm(data = shrub, weighted_n ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(shrub_n) # NEED TO DO MODEL AVERAGING
shrub_n  <- glm(data = shrub, weighted_n ~ treatment, family = gaussian, na.action = na.fail)

simulateResiduals(shrub_n, plot= T) # fine
shapiro.test(residuals(shrub_n)) # normal

summary(shrub_n)
emmeans(shrub_n, pairwise ~ treatment)
```
##### v.seed mass
```{r}
shrub_seed_mass <- glm(data = shrub, weighted_seed_mass ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(shrub_seed_mass) # NEED TO DO MODEL AVERAGING
shrub_seed_mass  <- glm(data = shrub, weighted_seed_mass ~ climate + treatment, family = gaussian, na.action = na.fail)

simulateResiduals(shrub_seed_mass, plot= T) # bad
shapiro.test(residuals(shrub_seed_mass)) # normal

summary(shrub_n)
emmeans(shrub_n, pairwise ~ treatment)

```
