---
title: "Functional Trait Models"
author: "Maggie Klope"
date: "10/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(stats)
library(sjPlot)
library(FD)
library(DHARMa) #model diagnostics
library(glmmTMB) #model fitting
library(MuMIn) #model summaries and comparisons
library(emmeans) #post-hoc analyses
# library(performance) #for R2 values

# Loading 2019 abundance data calculated from transect surveys
abund_2019 <-  read_csv("Datasheets/2019_abundance_sci_names.csv") %>% 
  rename(species_name = Species) %>% #changing column names
  rename(climate = Climate) %>% #changing column names
  rename(treatment = Plot)#changing column names

abund_2019$climate[abund_2019$climate == "Int"] <- "Intermediate" #changing name of int climate

# Loading 2019 functional trait data (currently only has LA)
traits_19 <- read_csv("Datasheets/temp_2019_traits.csv") %>% 
  rename(old_names = Species) %>% #changing column names
  rename(Species = sci_name) %>% #changing column names
  select(Climate, Treatment, Block, Species, LA) %>% 
  mutate(LA = as.numeric(LA)) %>% #making sure value is numeric
  mutate(Species = ifelse(Species == "Trifolium microcephalum", #fixing a typo that makes factors weird
                          "trifolium microcephalum",
                          Species)) %>%
  mutate(Treatment = ifelse(Treatment == "open", "Open", Treatment)) #same thing, a typo

abund_2019$climate[abund_2019$climate == "Int"] <- "Intermediate"#changing name of int climate

# Loading 2017 functional trait data
# traits_17 <- read_csv("final_traits_and_abundances.csv")

# TRY Database search to fill in missing species
# TRY_DB <- read_csv("Datasheets/TRY_DB_june_2020.csv") %>% 
#   filter(ValueKindName == c("Single", "Mean", "Best estimate")) %>% 
#   #unique() %>% 
#   dplyr::group_by(TraitName, AccSpeciesName) %>%
#   summarize(mean_value = mean(StdValue)) %>% 
#   rename(species_name = AccSpeciesName)

# write_csv(TRY_DB, "TRY_DB_summary.csv")

# reading in 2017 functional trait datasheet
md <- read_csv("Datasheets/MasterDataSheet(10_18_2020).csv") %>% 
  select(climate, treatment, species_name, individual, wet_weight_g, wet_weight_mg, dry_weight_g, dry_weight_mg, Area_Leaf_total_mm2, Average_Leaf_Area) %>% 
  mutate(wet_weight_mg = as.numeric(wet_weight_mg)) %>% 
  mutate(wet_weight_g = as.numeric(wet_weight_g)) %>% 
  mutate(dry_weight_g = as.numeric(dry_weight_g)) %>% 
  mutate(dry_weight_mg = as.numeric(dry_weight_mg)) %>% 
  mutate(leaf_area = as.numeric(Average_Leaf_Area)) %>% 
  mutate(sla = Area_Leaf_total_mm2 / dry_weight_mg) %>% #computing sla
  mutate(ldmc = dry_weight_mg / wet_weight_g) #computing ldmc

#finding average values for 2017 from the masterdatasheet
traits_2017 <- md %>% 
  group_by(climate, treatment, species_name) %>% 
  summarise_all(mean, na.rm = TRUE)
#changing treatment names
traits_2017$treatment[traits_2017$treatment == "Cattle Exclosure"] <- "Partial"
traits_2017$treatment[traits_2017$treatment == "Control"] <- "Open"
traits_2017$treatment[traits_2017$treatment == "Full Exclosure"] <- "Total"
# changing climate names
traits_2017$climate[traits_2017$climate == "Semi-arid"] <- "Intermediate"

#need to rename some species to match 2019 abundance
traits_2017$species_name[traits_2017$species_name == "Trifolium microcephalum"] <- "Trifolium sp."
traits_2017$species_name[traits_2017$species_name == "lupinus bicolor?"] <- "Lupinus bicolor"
traits_2017$species_name[traits_2017$species_name == "Erodium cicutarium"] <- "Erodium sp."
traits_2017$species_name[traits_2017$species_name == "Erodium brachycarpum"] <- "Erodium sp."
traits_2017$species_name[traits_2017$species_name == "Ribes sp."] <- "Ribes californicum var. hesperium"
traits_2017$species_name[traits_2017$species_name == "Melica imperfecta"] <- "Melica californica"
traits_2017$species_name[traits_2017$species_name == "Plagiobothrys nothofulvus"] <- "Plagiobothrys sp."

#combining 2017 trait data with 2019 abundance data
cwm_traits <- abund_2019 %>% 
  group_by(climate, treatment) %>% 
  left_join(traits_2017, by = c("climate", "treatment", "species_name")) %>% 
  select(climate, treatment, Block, species_name, Abundance, leaf_area, sla, ldmc, Notes)

other_traits <- read_csv("Datasheets/seed_mass_leaf_N.csv")

#data (updated) for Community-weighted means (CWMs)
cwm_traits_adj <-  read_csv("Datasheets/cwm_traits_updated.csv") %>% 
  left_join(other_traits, by = "species_name") %>% 
  mutate(weighted_la = leaf_area * Abundance) %>% #multiplying trait values by species abundance
  mutate(weighted_sla = sla * Abundance) %>% 
  mutate(weighted_ldmc = ldmc * Abundance) %>%
  mutate(weighted_seed_mass = seed_mass * Abundance) %>%
  mutate(weighted_n = leaf_n * Abundance) %>%
  group_by(climate, treatment, Block) %>% #grouping by climate, treatment, and block
  summarise_all(mean, na.rm = TRUE) %>% #finding the mean
  select(climate, treatment, Block, weighted_la, weighted_sla, weighted_ldmc, weighted_seed_mass, weighted_n)


```

## GLMs for individual species change

- Does not include block because I only have the mean for each species at each plot
- Some species are present in all climate/treatment, but some are not
- Some species could be done with an lm after a log transformation

### Models:

**What is the effect of climate and grazing on individual species trait changes?**

`glm(trait ~ Climate * Treatment, family = gaussian)`

- planning to do for LA, SLA, and LDMC (from field collection in 2019) for a subset of species
- could do for seed mass and leaf N, but those values would be from TRY Database
- species chosen as those that are present across as many climate/treatment combinations as possible
- unfortunately, I scanned and weighed the leaves together to get averages, so I have lost the ability to add block to my models
- need to think of how I would deal with multiple comparisons (bonferroni correction?)

```{r}
#writing function to take species name and test model with dredge

model_test <- function(species_name){
  temp_data <- traits_19[traits_19$Species == species_name,]
  glm <- glmmTMB(data = temp_data, LA ~ Climate * Treatment, family = gaussian)
  print(dredge(glm))
}

```

#### Bromus diandrus

- invasive grass
- no difference in LA between climate treatments
- model summary says that mesic is significantly lower than Arid, but that doesn't show when I use emmeans

```{r}
model_test("Bromus diandrus") #best model includes only intercept, but including climate also within AIC range

bro_dia <- traits_19[traits_19$Species == "Bromus diandrus",]
glm_bro_dia <- glmmTMB(data = bro_dia, LA ~ Climate, family = gaussian)

simulateResiduals(glm_bro_dia, plot= T) # qq plot doesn't look that great
shapiro.test(residuals(glm_bro_dia)) # but residuals are normal (barely)

summary(glm_bro_dia) # shows difference between Arid and Mesic
emmeans(glm_bro_dia, pairwise ~ Climate) #but emmeans doesn't show a significant difference...
```

#### Festuca myuros

- non-native grass
- log transformed
- Arid > Intermediate
- Arid > Mesic
- No significant difference between Int and Mesic

```{r}
# model_test("Festuca myuros") #get model convergence error

fes_myu <- traits_19[traits_19$Species == "Festuca myuros",]
glm_fes_myu <- glmmTMB(data = fes_myu, LA ~ Climate + Treatment,  family = gaussian) # trying without interaction
dredge(glm_fes_myu) # remove treatment from model
glm_fes_myu <- glmmTMB(data = fes_myu, LA ~ Climate,  family = gaussian)

simulateResiduals(glm_fes_myu, plot=T)
shapiro.test(residuals(glm_fes_myu)) #not normal

# using log transformation
fes_myu <- fes_myu %>% 
  mutate(log_LA = log(LA))

# log_fes_myu <- glmmTMB(data = fes_myu, log_LA ~ Climate * Treatment,  family = gaussian) # convergence error
log_fes_myu <- glmmTMB(data = fes_myu, log_LA ~ Climate + Treatment,  family = gaussian)
dredge(log_fes_myu) #drop treatment
log_fes_myu <- glmmTMB(data = fes_myu, log_LA ~ Climate,  family = gaussian)

simulateResiduals(log_fes_myu, plot=T)
shapiro.test(residuals(log_fes_myu)) #normal

summary(log_fes_myu)
log_fes_myu_em <- emmeans(log_fes_myu, ~Climate)
pairs(log_fes_myu_em)

```

#### Bromus diandrus
```{r}
model_test("Bromus hordeaceus") #need to do averaging

bro_ho <- traits_19[traits_19$Species == "Bromus hordeaceus",]

glm_bro_ho <- glmmTMB(data = bro_ho, LA ~ Climate * Treatment, family = gaussian)
dredge(glm_bro_ho) #need to do averaging

```

#### Bromus tectorum

- invasive grass

```{r}
bro_tec <- traits_19[traits_19$Species == "Bromus tectorum",]

glm_bro_tec <- glmmTMB(data = bro_tec, LA ~ Climate * Treatment, family = gaussian)
dredge(glm_bro_tec) # what do you do when best model only includes intercept?

```

#### Hordeum murium

- invasive grass
- model only includes Treatment
- Total > Partial

```{r}
hor_mur <- traits_19[traits_19$Species == "Hordeum murinum",]

# glm_hor_mur <- glmmTMB(data = hor_mur, LA ~ Climate * Treatment, family = gaussian) #convergence
glm_hor_mur <- glmmTMB(data = hor_mur, LA ~ Climate + Treatment, family = gaussian)
dredge(glm_hor_mur) # best fit includes treatment only
glm_hor_mur <- glmmTMB(data = hor_mur, LA ~ Treatment, family = gaussian)

# does data fit model?
simulateResiduals(glm_hor_mur, plot=T) # doesn't look that great
shapiro.test(residuals(glm_hor_mur)) # but residuals are normal

# model results
summary(glm_hor_mur)
emmeans(glm_hor_mur, pairwise ~ Treatment)

```

#### Erodium cicutarium

- invasive forb

```{r}

ero_cic <- traits_19[traits_19$Species == "Erodium cicutarium",]

glm_ero_cic <- glmmTMB(data = ero_cic, LA ~ Climate * Treatment, family = gaussian)
dredge(glm_ero_cic) # best model includes intercept only, but model with climate also has similar AIC value
glm_ero_cic <- glmmTMB(data = ero_cic, LA ~ Climate, family = gaussian)

# does data fit model?
simulateResiduals(glm_ero_cic, plot=T) # really messed up

```

#### Galium aparine

- native forb

```{r}

model_test("Galium aparine") #get convergence

gal_apa <- traits_19[traits_19$Species == "Galium aparine",]
glm_gal_apa <- glmmTMB(data = gal_apa, LA ~ Climate * Treatment, family = gaussian)
dredge(glm_gal_apa) #best model does not include treatment
glm_gal_apa <- glmmTMB(data = gal_apa, LA ~ Climate, family = gaussian)

simulateResiduals(glm_gal_apa, plot=T)
shapiro.test(residuals(glm_gal_apa)) # normal

summary(glm_gal_apa)
emmeans(glm_gal_apa, pairwise ~ Climate)

```

```{r}
# Plagiobothrys nothofulvus (forb)
glm_pla_not <- glm(data = traits_19[traits_19$Species == "Plagiobothrys nothofulvus",], LA ~ Climate * Treatment, family = gaussian)

# Ribes californicum var. hesperium (shrub)
glm_ribes <- glm(data = traits_19[traits_19$Species == "Ribes californicum var. hesperium",], LA ~ Climate * Treatment, family = gaussian)

# Symphoricarpos_mollis (shrub)
glm_sym_mol <- glm(data = traits_19[traits_19$Species == "Symphoricarpos_mollis",], LA ~ Treatment, family = gaussian) #only at Mesic climate

# Ericameria nauseosa (shrub)
glm_eri_nau <- glm(data = traits_19[traits_19$Species == "Ericameria nauseosa",], LA ~ Climate * Treatment, family = gaussian)
```

## By functional group

```{r}



```


```{r}
# # TRY Database search to fill in missing species
# TRY_DB_1 <- read_csv("Datasheets/TRY_DB_june_2020.csv") %>% 
#   filter(ValueKindName %in% c("Single", "Mean", "Best estimate")) %>%
#   select(AccSpeciesName, TraitName, StdValue) %>% 
#   dplyr::group_by(AccSpeciesName, TraitName) %>% 
#   mutate(StdValue = as.numeric(StdValue)) %>% 
#   summarize(mean = mean(StdValue)) %>% 
#   rename(species_name = AccSpeciesName)
# 
# TRY_DB_2 <- read_csv("Datasheets/TRY_DB_Oct-18-20.csv") %>% 
#   filter(ValueKindName %in% c("Single", "Mean", "Best estimate")) %>%
#   select(AccSpeciesName, TraitName, StdValue) %>% 
#   dplyr::group_by(AccSpeciesName, TraitName) %>% 
#   mutate(StdValue = as.numeric(StdValue)) %>% 
#   summarize(mean = mean(StdValue)) %>% 
#   rename(species_name = AccSpeciesName)
# 
# write.csv(TRY_DB_2, "TRY_DB_2.csv")

```

