---
title: "Functional Group Models"
author: "Maggie Klope"
date: "1/19/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(stats)
library(sjPlot)
library(FD)
library(DHARMa) #model diagnostics
library(glmmTMB) #model fitting
library(MuMIn) #model summaries and comparisons
library(emmeans) #post-hoc analyses
library(gt)
library(tibble)
library(lsmeans)
library(gridExtra)
library(multcomp)
library(car)
library(ggeffects)

other_traits <- read_csv("~/github/Tejon_Functional_Traits/Datasheets/seed_mass_leaf_N.csv")

cwm_traits_adj <-  read_csv("~/github/Tejon_Functional_Traits/Datasheets/cwm_traits_updated.csv") %>%
  left_join(other_traits, by = "species_name") %>%
  mutate(weighted_la = leaf_area * Abundance) %>% #multiplying trait values by species abundance
  mutate(weighted_sla = sla * Abundance) %>%
  mutate(weighted_ldmc = ldmc * Abundance) %>%
  mutate(weighted_seed_mass = seed_mass * Abundance) %>%
  mutate(weighted_n = leaf_n * Abundance) %>%
  group_by(climate, treatment, Block) %>% #grouping by climate, treatment, and block
  summarise_all(mean, na.rm = TRUE) %>% #finding the mean
  dplyr::select(climate, treatment, Block, weighted_la, weighted_sla, weighted_ldmc, weighted_seed_mass, weighted_n)

# log transformation for seed mass & leaf n
# cwm_traits_adj <- cwm_traits_adj %>% 
#   mutate(log_seed_mass = log(weighted_seed_mass)) %>% 
#   mutate(log_n = log(weighted_n))

```

```{r, include=FALSE}
functional_avg <-  read_csv("~/github/Tejon_Functional_Traits/Datasheets/cwm_traits_updated.csv") %>%
  left_join(other_traits, by = "species_name") %>% 
  group_by(climate, Block, treatment, functional_group) %>%
  summarise_all(mean, na.rm = TRUE) %>% #finding the mean
  dplyr::select(Block, climate, treatment, functional_group, leaf_area, sla, ldmc, seed_mass, leaf_n)

functional_data <- read_csv("~/github/Tejon_Functional_Traits/Datasheets/cwm_traits_updated.csv") %>%
  left_join(other_traits, by = "species_name") %>% 
  dplyr::select(Block, climate, treatment, functional_group, leaf_area, sla, ldmc, seed_mass, leaf_n)

# cwm_functional_2 <- read_csv("~/github/Tejon_Functional_Traits/Datasheets/cwm_traits_updated.csv") %>% 
#   left_join(other_traits, by = "species_name") %>% 
#   dplyr::select(climate, treatment, Block, functional_group, Abundance) %>% 
#   dplyr::filter(Block == "A" | Block ==  "D" | Block ==  "G") %>% 
#   group_by(climate, functional_group) %>% 
#   summarise(Total_Abundance = sum(Abundance))
# 
# ggplot(cwm_functional_2, aes(x = "", y = Total_Abundance, fill = functional_group)) +
#   geom_bar(stat="identity", width=1, color = "white") +
#   coord_polar("y", start = 0) +
#   facet_wrap(~climate) +
#   theme_void() +
#   labs(fill = "Functional Group:") +
#   scale_fill_manual(values = c("#c7eae5", "#b8e186", "#dfc27d")) +
#   theme(plot.background = element_rect(fill = "transparent", color = NA),
#         legend.background = element_rect(fill = "white", size = 0)) +
#   theme(legend.position="bottom")
  
# ggsave("plant_communit_piechart.png", path = "~/github/Tejon_Functional_Traits/Figures", width = 9, height = 7, bg = "transparent")

#  barplot showing all climate/treatments
cwm_functional %>%
  pivot_longer(cols = leaf_area:leaf_n,
               names_to = "traits",
               values_to = "value") %>%
  ggplot(aes(x = climate, y = value, color = treatment)) +
  geom_boxplot() +
  theme_bw() +
  facet_grid(traits ~ functional_group, scales = "free")

# ggsave("cwm_by_functional_group_barchart.png", path = "~/github/Tejon_Functional_Traits/Figures", width = 9, height = 7, bg = "transparent")

# grass <- cwm_functional %>% 
#   filter(functional_group == "grass")
# 
# forb <- cwm_functional %>% 
#   filter(functional_group == "forb") %>% 
#   mutate(sqrt_la = sqrt(weighted_la))
# 
# shrub <- cwm_functional %>% 
#   filter(functional_group == "shrub")
  
```

#### Do trait averages within functional group vary by climate and herbivore treatment?

- Do I do one model for each functional group's trait?
Ex: grass leaf area ~ climate + treatment?

- Or can I do one model per trait and look to see if interaction between functional group and/or climate is included?
Ex: leaf area ~ climate + treatment + functional group + climate:functional group + climate:treatment?

- Note: I don't have a large enough sample size to include block as a random effect with the single model approach

##### 1. leaf area

###### a. one-model
```{r, warning=FALSE}
#### raw data ###
la_data <- functional_data %>% 
  dplyr::select(Block, climate, treatment, functional_group, leaf_area) %>% 
  drop_na() %>%
  mutate(log_la = log(leaf_area)) %>% 
  mutate(sqrt_la = sqrt(leaf_area)) %>% 
  mutate(sqrt_la_plus = sqrt(leaf_area + 1))

# un-transformed data
funct_la <- glmmTMB(data = la_data, leaf_area ~ climate * functional_group * treatment, family = gaussian, na.action = na.fail)
dredge(funct_la)
funct_la <- glmmTMB(data = la_data, leaf_area ~ functional_group + treatment, family = gaussian, na.action = na.fail)

simulateResiduals(funct_la, plot= T) # bad

#trying log transformation
funct_la <- glmmTMB(data = la_data, log_la ~ climate *  functional_group * treatment, family = gaussian, na.action = na.fail)
dredge(funct_la)
funct_la <- glmmTMB(data = la_data, log_la ~ climate +  functional_group + treatment + climate:functional_group + treatment:functional_group, family = gaussian, na.action = na.fail)

simulateResiduals(funct_la, plot= T) # bad

# square root transformation
funct_la <- glmmTMB(data = la_data, sqrt_la ~ climate *  functional_group * treatment , family = gaussian, na.action = na.fail)
dredge(funct_la)
funct_la <- glmmTMB(data = la_data, sqrt_la ~ treatment , family = gaussian, na.action = na.fail)

simulateResiduals(funct_la, plot= T) # bad
shapiro.test(residuals(funct_la)) # not normal

# square root +1 transformation
funct_la <- glmmTMB(data = la_data, sqrt_la_plus ~ climate *  functional_group * treatment , family = gaussian, na.action = na.fail)
dredge(funct_la)
funct_la <- glmmTMB(data = la_data, sqrt_la_plus ~ treatment , family = gaussian, na.action = na.fail)

simulateResiduals(funct_la, plot= T) # bad
shapiro.test(residuals(funct_la)) # not normal

### avg data ###
funct_la <- glmmTMB(data = functional_avg, leaf_area ~ climate * functional_group * treatment, family = gaussian, na.action = na.fail)
dredge(funct_la)
funct_la <- glmmTMB(data = functional_avg, leaf_area ~ climate + functional_group + treatment + climate:functional_group + functional_group:treatment, family = gaussian, na.action = na.fail)
simulateResiduals(funct_la, plot= T) # bad

# log transformation
functional_avg <- functional_avg %>% 
  mutate(log_la = log(leaf_area)) %>% 
  mutate(sqrt_la = sqrt(leaf_area))

funct_la <- glmmTMB(data = functional_avg, log_la ~ climate * functional_group * treatment, family = gaussian, na.action = na.fail)
dredge(funct_la)
funct_la <- glmmTMB(data = functional_avg, leaf_area ~ climate + functional_group + treatment + climate:functional_group, family = gaussian, na.action = na.fail)
simulateResiduals(funct_la, plot= T) # bad

# square root transformation
funct_la <- glmmTMB(data = functional_avg, sqrt_la ~ climate * functional_group * treatment, family = gaussian, na.action = na.fail)
dredge(funct_la)
funct_la <- glmmTMB(data = functional_avg, sqrt_la ~ climate + functional_group + treatment + climate:functional_group + climate:treatment + functional_group:treatment, family = gaussian, na.action = na.fail)
simulateResiduals(funct_la, plot= T) # bad
shapiro.test(residuals(funct_la )) # not normal
```

###### b. grass
```{r, warning=FALSE}
# using raw data
grass_la_data <- functional_data %>% 
  filter(functional_group == "grass") %>% 
  dplyr::select(Block, climate, treatment, functional_group, leaf_area) %>% 
  mutate(log_la = log(leaf_area)) %>% 
  mutate(sqrt_la = sqrt(leaf_area))

grass_funct_la <- glmmTMB(data = grass_la_data, leaf_area ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(grass_funct_la)
grass_funct_la <- glmmTMB(data = grass_la_data, leaf_area ~ 1 + (1|Block), family = gaussian, na.action = na.fail)

simulateResiduals(grass_funct_la, plot= T) # not good

# log transformation
grass_funct_la <- glmmTMB(data = grass_la_data, log_la ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(grass_funct_la)
grass_funct_la <- glmmTMB(data = grass_la_data, log_la ~ climate + (1|Block), family = gaussian, na.action = na.fail)

shapiro.test(residuals(grass_funct_la)) # not normal

# square root transformation
grass_funct_la <- glmmTMB(data = grass_la_data, sqrt_la ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(grass_funct_la)
grass_funct_la <- glmmTMB(data = grass_la_data, sqrt_la ~ climate + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(grass_funct_la, plot= T) # not good

# using averaged data
grass_la_avg <- functional_avg %>% 
  filter(functional_group == "grass") %>% 
  dplyr::select(Block, climate, treatment, functional_group, leaf_area) %>% 
  mutate(log_la = log(leaf_area)) %>% 
  mutate(sqrt_la = sqrt(leaf_area))

grass_funct_la <- glmmTMB(data = grass_la_avg, leaf_area ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(grass_funct_la )
simulateResiduals(grass_funct_la, plot= T) # good
shapiro.test(residuals(grass_funct_la))

```
###### c. shrub
```{r, warning=FALSE}
# using averaged data
shrub_la_avg <- functional_avg %>% 
  filter(functional_group == "shrub") %>% 
  dplyr::select(Block, climate, treatment, functional_group, leaf_area) %>% 
  mutate(log_la = log(leaf_area)) %>% 
  mutate(sqrt_la = sqrt(leaf_area))

shrub_funct_la <- glmmTMB(data = shrub_la_avg, leaf_area ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(shrub_funct_la )
shrub_funct_la <- glmmTMB(data = shrub_la_avg, leaf_area ~ climate + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(shrub_funct_la, plot= T) # doesn't look that great
shapiro.test(residuals(shrub_funct_la)) # but residuals are normal
```
######d. forb
```{r, warning=FALSE}
# using averaged data
forb_la_avg <- functional_avg %>% 
  filter(functional_group == "forb") %>% 
  dplyr::select(Block, climate, treatment, functional_group, leaf_area) %>% 
  mutate(log_la = log(leaf_area)) %>% 
  mutate(sqrt_la = sqrt(leaf_area))

forb_funct_la <- glmmTMB(data = forb_la_avg, leaf_area ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(forb_funct_la )
forb_funct_la <- glmmTMB(data = forb_la_avg, leaf_area ~ 1 + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(forb_funct_la, plot= T) # doesn't look that great
shapiro.test(residuals(forb_funct_la)) # not normal

forb_funct_la <- glmmTMB(data = forb_la_avg, log_la ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(forb_funct_la )
forb_funct_la <- glmmTMB(data = forb_la_avg, log_la ~  treatment + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(forb_funct_la, plot= T) # good
shapiro.test(residuals(forb_funct_la)) # normal

```
##### 2. specific leaf area
```{r, warning=FALSE}
sla_data <- functional_data %>% 
  dplyr::select(Block, climate, treatment, functional_group, sla) %>% 
  drop_na() %>% 
  mutate(log_sla = log(sla))

funct_sla <- glmmTMB(data = sla_data, sla ~ climate * functional_group * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(funct_sla)
funct_sla <- glmmTMB(data = sla_data, sla ~ treatment + functional_group + (1|Block), family = gaussian, na.action = na.fail)

simulateResiduals(funct_la, plot= T) # bad

# log transformation
funct_sla <- glmmTMB(data = sla_data, log_sla ~ climate * functional_group * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(funct_sla)
funct_sla <- glmmTMB(data = sla_data, log_sla ~ functional_group + (1|Block), family = gaussian, na.action = na.fail)

simulateResiduals(funct_la, plot= T) # bad

# using average data
funct_sla <- glmmTMB(data = functional_avg, sla ~ climate * treatment * functional_group + (1|Block), family = gaussian, na.action = na.fail)
# funct_sla <- glmmTMB(data = sla_data, sla ~ climate + treatment + functional_group + climate:functional_group + treatment + functional_group + (1|Block), family = gaussian, na.action = na.fail)

dredge(funct_sla)
funct_sla <- glmmTMB(data = functional_avg, sla ~ climate + functional_group + treatment + climate:functional_group + climate:treatment + (1|Block), family = gaussian, na.action = na.fail)

simulateResiduals(funct_sla, plot= T) # good
shapiro.test(residuals(funct_sla)) # normal
```
###### b. grass
```{r, warning=FALSE}
# using raw data
grass_sla_data <- functional_data %>% 
  filter(functional_group == "grass") %>% 
  dplyr::select(Block, climate, treatment, functional_group, sla) %>% 
  mutate(log_sla = log(sla)) %>% 
  mutate(sqrt_sla = sqrt(sla))

grass_funct_sla <- glmmTMB(data = grass_sla_data, sla ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(grass_funct_sla)

simulateResiduals(grass_funct_sla, plot= T) # ok?
shapiro.test(residuals(grass_funct_sla)) # not normal

# using averaged data
grass_sla_avg <- functional_avg %>% 
  filter(functional_group == "grass") %>% 
  dplyr::select(Block, climate, treatment, functional_group, sla) %>% 
  mutate(log_sla = log(sla)) %>% 
  mutate(sqrt_sla = sqrt(sla))

grass_funct_sla <- glmmTMB(data = grass_sla_avg, sla ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(grass_funct_sla )
simulateResiduals(grass_funct_sla, plot= T) # good
shapiro.test(residuals(grass_funct_sla))
```

###### c. shrub
```{r, warning=FALSE}
# using raw data
shrub_sla_data <- functional_data %>% 
  filter(functional_group == "shrub") %>% 
  dplyr::select(Block, climate, treatment, functional_group, sla) %>% 
  mutate(log_sla = log(sla)) %>% 
  mutate(sqrt_sla = sqrt(sla))

shrub_funct_sla <- glmmTMB(data = shrub_sla_data, sla ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(shrub_funct_sla)
shrub_funct_sla <- glmmTMB(data = shrub_sla_data, sla ~ 1 + (1|Block), family = gaussian, na.action = na.fail)

simulateResiduals(shrub_funct_sla, plot= T) # ok?
shapiro.test(residuals(shrub_funct_sla)) # not normal

# using averaged data
shrub_sla_avg <- functional_avg %>% 
  filter(functional_group == "shrub") %>% 
  dplyr::select(Block, climate, treatment, functional_group, sla) %>% 
  mutate(log_sla = log(sla)) %>% 
  mutate(sqrt_sla = sqrt(sla))

shrub_funct_sla <- glmmTMB(data = shrub_sla_avg, sla ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(shrub_funct_sla )
simulateResiduals(shrub_funct_sla, plot= T) # not good

shrub_funct_sla <- glmmTMB(data = shrub_sla_avg, log_sla ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(shrub_funct_sla)
simulateResiduals(shrub_funct_sla, plot= T) # not good

```
###### c. forb
```{r, warning=FALSE}
# using raw data
forb_sla_data <- functional_data %>% 
  filter(functional_group == "forb") %>% 
  dplyr::select(Block, climate, treatment, functional_group, sla) %>% 
  drop_na() %>% 
  mutate(log_sla = log(sla)) %>% 
  mutate(sqrt_sla = sqrt(sla))

forb_funct_sla <- glmmTMB(data = forb_sla_data, sla ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(forb_funct_sla)
forb_funct_sla <- glmmTMB(data = forb_sla_data, sla ~ 1 + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(forb_funct_sla, plot= T) # not good

# log transformed
forb_funct_sla <- glmmTMB(data = forb_sla_data, log_sla ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(forb_funct_sla)
forb_funct_sla <- glmmTMB(data = forb_sla_data, log_sla ~ 1 + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(forb_funct_sla, plot= T) # good

# using averaged data
forb_sla_avg <- functional_avg %>% 
  filter(functional_group == "forb") %>% 
  dplyr::select(Block, climate, treatment, functional_group, sla) %>% 
  mutate(log_sla = log(sla)) %>% 
  mutate(sqrt_sla = sqrt(sla))

forb_funct_sla <- glmmTMB(data = forb_sla_avg, sla ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(forb_funct_sla )
simulateResiduals(forb_funct_sla, plot= T) # good
shapiro.test(residuals(forb_funct_sla)) # not normal
```
##### 3. ldmc
```{r, warning=FALSE}
cwm_functional <- cwm_functional %>% 
  mutate(log_ldmc = log(weighted_ldmc))

funct_ldmc <- glmmTMB(data = cwm_functional, weighted_ldmc ~ climate * functional_group + treatment * functional_group + (1|Block), family = gaussian, na.action = na.fail)
dredge(funct_ldmc)
funct_ldmc <- glmmTMB(data = cwm_functional, weighted_ldmc ~ climate + functional_group + treatment + climate:functional_group + functional_group:treatment + (1|Block), na.action = na.fail)

simulateResiduals(funct_ldmc, plot= T) # Not good

# log transformation
funct_ldmc <- glmmTMB(data = cwm_functional, log_ldmc ~ climate * functional_group + treatment * functional_group + (1|Block), family = gaussian, na.action = na.fail)
dredge(funct_ldmc)
funct_ldmc <- glmmTMB(data = cwm_functional, log_ldmc ~ climate + functional_group + treatment + climate:functional_group + functional_group:treatment + (1|Block), na.action = na.fail)

simulateResiduals(funct_ldmc, plot= T) # ok
shapiro.test(residuals(funct_ldmc)) # normal

# pairwise comparisons
emmeans(funct_ldmc, pairwise ~ functional_group)
emmeans(funct_ldmc, pairwise ~ treatment | functional_group)
emmeans(funct_ldmc, pairwise ~ climate | functional_group)

```
###### b. grass
```{r}
# using raw data
grass_ldmc_data <- functional_data %>% 
  filter(functional_group == "grass") %>% 
  dplyr::select(Block, climate, treatment, functional_group, ldmc) %>% 
  mutate(log_ldmc = log(ldmc)) %>% 
  mutate(sqrt_ldmc = sqrt(ldmc))

grass_funct_ldmc <- glmmTMB(data = grass_ldmc_data, ldmc ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(grass_funct_ldmc)
grass_funct_ldmc <- glmmTMB(data = grass_ldmc_data, ldmc ~ climate + treatment + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(grass_funct_ldmc, plot= T) # not ok

# log transformation
grass_funct_ldmc <- glmmTMB(data = grass_ldmc_data, log_ldmc ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(grass_funct_ldmc)
simulateResiduals(grass_funct_ldmc, plot= T) # groups do not have equal variance

```
###### c. shrub
```{r, warning=FALSE}
# using raw data
shrub_ldmc_data <- functional_data %>% 
  filter(functional_group == "shrub") %>% 
  dplyr::select(Block, climate, treatment, functional_group, ldmc) %>% 
  mutate(log_ldmc = log(ldmc)) %>% 
  mutate(sqrt_ldmc = sqrt(ldmc))

shrub_funct_ldmc <- glmmTMB(data = shrub_ldmc_data, ldmc ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(shrub_funct_ldmc)
shrub_funct_ldmc <- glmmTMB(data = shrub_ldmc_data, ldmc ~ climate + (1|Block), family = gaussian, na.action = na.fail)

simulateResiduals(shrub_funct_ldmc, plot= T) # ok?
shapiro.test(residuals(shrub_funct_ldmc)) # normal

```
###### c. forb
```{r, warning=FALSE}
# using raw data
forb_ldmc_data <- functional_data %>% 
  filter(functional_group == "forb") %>% 
  dplyr::select(Block, climate, treatment, functional_group, ldmc) %>% 
  drop_na() %>% 
  mutate(log_ldmc = log(ldmc)) %>% 
  mutate(sqrt_ldmc = sqrt(ldmc))

forb_funct_ldmc <- glmmTMB(data = forb_ldmc_data, ldmc ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(forb_funct_ldmc)
forb_funct_ldmc <- glmmTMB(data = forb_ldmc_data, ldmc ~ treatment + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(forb_funct_ldmc, plot= T) # good
```

##### 4. lnc
```{r, warning=FALSE}
funct_n <- glmmTMB(data = cwm_functional, weighted_n ~ climate * functional_group + treatment * functional_group + (1|Block), family = gaussian, na.action = na.fail)
dredge(funct_n)
funct_n <- glmmTMB(data = cwm_functional, weighted_n ~ climate + functional_group + treatment + climate:functional_group + functional_group:treatment + (1|Block), na.action = na.fail)

simulateResiduals(funct_n, plot= T) # not good

cwm_functional <- cwm_functional %>% 
  mutate(log_n = log(weighted_n)) %>% 
  mutate(log_plus_n = log(weighted_n+1))

# trying log transformation with gaussian
funct_n <- glmmTMB(data = cwm_functional, log_n ~ climate * functional_group + treatment * functional_group + (1|Block), family = gaussian, na.action = na.fail)
dredge(funct_n)
funct_n <- glmmTMB(data = cwm_functional, log_n ~ climate + functional_group + treatment + climate:functional_group + (1|Block), na.action = na.fail)

simulateResiduals(funct_n, plot= T) # looks good
shapiro.test(residuals(funct_n)) # not normal - is that ok?

# # trying log(n+1) transformation with gaussian
# funct_n <- glm(data = cwm_functional, log_plus_n ~ climate * treatment * functional_group, family = gaussian, na.action = na.fail)
# dredge(funct_n)
# funct_n <- glm(data = cwm_functional, log_plus_n ~ climate + functional_group + treatment + climate:functional_group, family = gaussian, na.action = na.fail)
# 
# simulateResiduals(funct_n, plot= T) # looks ok
# shapiro.test(residuals(funct_n)) # normal

# pairwise comparisons
emmeans(funct_n, pairwise ~ functional_group)
emmeans(funct_n, pairwise ~ treatment | functional_group)
emmeans(funct_n, pairwise ~ climate | functional_group)

```
###### b. grass
```{r}
# using raw data
grass_leaf_n_data <- functional_data %>% 
  filter(functional_group == "grass") %>% 
  dplyr::select(Block, climate, treatment, functional_group, leaf_n) %>% 
  mutate(log_leaf_n = log(leaf_n)) %>% 
  mutate(sqrt_leaf_n = sqrt(leaf_n))

grass_funct_leaf_n <- glmmTMB(data = grass_leaf_n_data, leaf_n ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(grass_funct_leaf_n)
grass_funct_leaf_n <- glmmTMB(data = grass_leaf_n_data, leaf_n ~ climate + treatment + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(grass_funct_leaf_n, plot= T) # good
```
###### c. shrub
```{r, warning=FALSE}
# using raw data
shrub_leaf_n_data <- functional_data %>% 
  filter(functional_group == "shrub") %>% 
  dplyr::select(Block, climate, treatment, functional_group, leaf_n) %>% 
  mutate(log_leaf_n = log(leaf_n)) %>% 
  mutate(sqrt_leaf_n = sqrt(leaf_n))

shrub_funct_leaf_n <- glmmTMB(data = shrub_leaf_n_data, leaf_n ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(shrub_funct_leaf_n)
shrub_funct_leaf_n <- glmmTMB(data = shrub_leaf_n_data, leaf_n ~ climate + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(shrub_funct_leaf_n, plot= T) # not good

# log transformation
shrub_funct_leaf_n <- glmmTMB(data = shrub_leaf_n_data, log_leaf_n ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(shrub_funct_leaf_n)
shrub_funct_leaf_n <- glmmTMB(data = shrub_leaf_n_data, log_leaf_n ~ climate + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(shrub_funct_leaf_n, plot= T) # not good

# square root transformation
shrub_funct_leaf_n <- glmmTMB(data = shrub_leaf_n_data, sqrt_leaf_n ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(shrub_funct_leaf_n)
shrub_funct_leaf_n <- glmmTMB(data = shrub_leaf_n_data, leaf_n ~ climate + (1|Block), family = gaussian, na.action = na.fail)

simulateResiduals(shrub_funct_leaf_n, plot= T) # not good
shapiro.test(residuals(shrub_funct_leaf_n)) # normal

```
###### c. forb
```{r, warning=FALSE}
# using raw data
forb_leaf_n_data <- functional_data %>% 
  filter(functional_group == "forb") %>% 
  dplyr::select(Block, climate, treatment, functional_group, leaf_n) %>% 
  drop_na() %>% 
  mutate(log_leaf_n = log(leaf_n)) %>% 
  mutate(sqrt_leaf_n = sqrt(leaf_n))

forb_funct_leaf_n <- glmmTMB(data = forb_leaf_n_data, leaf_n ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(forb_funct_leaf_n)
forb_funct_leaf_n <- glmmTMB(data = forb_leaf_n_data, leaf_n ~ 1 + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(forb_funct_leaf_n, plot= T) # good
```

##### 5. seed mass
```{r, warning=FALSE}
# untransformed with gaussian
funct_seed_mass <- glmmTMB(data = cwm_functional, weighted_seed_mass ~ climate * functional_group + treatment * functional_group + (1|Block), family = gaussian, na.action = na.fail)
dredge(funct_seed_mass)
funct_seed_mass <- glmmTMB(data = cwm_functional, weighted_seed_mass ~ climate + functional_group + climate:functional_group + (1|Block), na.action = na.fail)

simulateResiduals(funct_seed_mass, plot= T) # bad

# log transformation with gaussian
cwm_functional <- cwm_functional %>% 
  mutate(log_seed_mass = log(weighted_seed_mass))

funct_seed_mass <- glmmTMB(data = cwm_functional, log_seed_mass ~ climate * functional_group + treatment * functional_group + (1|Block), family = gaussian, na.action = na.fail)
dredge(funct_seed_mass)
funct_seed_mass <- glmmTMB(data = cwm_functional,log_seed_mass ~ climate + functional_group + climate:functional_group + (1|Block), na.action = na.fail)

simulateResiduals(funct_seed_mass, plot= T) # ok
shapiro.test(residuals(funct_seed_mass)) # normal

# # for back transformation
# funct_seed_mass <- glm(data = cwm_functional, log(weighted_seed_mass) ~ climate + functional_group + climate:functional_group, na.action = na.fail)
# emmeans::contrast(funct_seed_mass)
# 
# funct_seed_mass_emm <- emmeans(funct_seed_mass, ~ climate + functional_group + climate:functional_group)
# summary(funct_seed_mass_emm) # results are given on a log scale
# summary(funct_seed_mass_emm, infer = TRUE, null = log(35), type = "response")
# 
# emmeans(funct_seed_mass, ~ climate)
# test_emm <- emmeans(funct_seed_mass, "climate", transform = "log", type = "response")
# 
# funct_seed_mass.rg <- update(ref_grid(funct_seed_mass), tran = make.tran("genlog", 1))
# 
# contrast(regrid(funct_seed_mass.rg))
# contrast(funct_seed_mass_emm)
# contrast(test_emm)

# pairwise comparisons
emmeans(funct_seed_mass, pairwise ~ functional_group)
emmeans(funct_seed_mass, pairwise ~ climate | functional_group)

```
###### b. grass
```{r}
# using raw data
grass_seed_mass_data <- functional_data %>% 
  filter(functional_group == "grass") %>% 
  dplyr::select(Block, climate, treatment, functional_group, seed_mass) %>% 
  mutate(log_seed_mass = log(seed_mass)) %>% 
  mutate(sqrt_seed_mass = sqrt(seed_mass))

grass_funct_seed_mass <- glmmTMB(data = grass_seed_mass_data, seed_mass ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(grass_funct_seed_mass)
grass_funct_seed_mass <- glmmTMB(data = grass_seed_mass_data, seed_mass ~ climate + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(grass_funct_seed_mass, plot= T) # not ok

# log transformation
grass_funct_seed_mass <- glmmTMB(data = grass_seed_mass_data, log_seed_mass ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(grass_funct_seed_mass)
grass_funct_seed_mass <- glmmTMB(data = grass_seed_mass_data, log_seed_mass ~ climate + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(grass_funct_seed_mass, plot= T) # groups do not have equal variance

# sqrt transformation
grass_funct_seed_mass <- glmmTMB(data = grass_seed_mass_data, sqrt_seed_mass ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(grass_funct_seed_mass)
grass_funct_seed_mass <- glmmTMB(data = grass_seed_mass_data, sqrt_seed_mass ~ climate + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(grass_funct_seed_mass, plot= T) # groups do not have equal variance; residuals not normal

```
###### c. shrub
```{r, warning=FALSE}
# using raw data
shrub_seed_mass_data <- functional_data %>% 
  filter(functional_group == "shrub") %>% 
  dplyr::select(Block, climate, treatment, functional_group, seed_mass) %>% 
  mutate(log_seed_mass = log(seed_mass)) %>% 
  mutate(sqrt_seed_mass = sqrt(seed_mass))

shrub_funct_seed_mass <- glmmTMB(data = shrub_seed_mass_data, seed_mass ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(shrub_funct_seed_mass)
shrub_funct_seed_mass <- glmmTMB(data = shrub_seed_mass_data, seed_mass ~ 1 + (1|Block), family = gaussian, na.action = na.fail)

simulateResiduals(shrub_funct_seed_mass, plot= T) # not good

# log transformation
shrub_funct_seed_mass <- glmmTMB(data = shrub_seed_mass_data, log_seed_mass ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(shrub_funct_seed_mass)
shrub_funct_seed_mass <- glmmTMB(data = shrub_seed_mass_data, log_seed_mass ~ climate + (1|Block), family = gaussian, na.action = na.fail)

simulateResiduals(shrub_funct_seed_mass, plot= T) # not good

# square root transformation
shrub_funct_seed_mass <- glmmTMB(data = shrub_seed_mass_data, sqrt_seed_mass ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(shrub_funct_seed_mass)
shrub_funct_seed_mass <- glmmTMB(data = shrub_seed_mass_data, sqrt_seed_mass ~ 1 + (1|Block), family = gaussian, na.action = na.fail)

simulateResiduals(shrub_funct_seed_mass, plot= T) # not good

```
###### c. forb
```{r, warning=FALSE}
# using raw data
forb_seed_mass_data <- functional_data %>% 
  filter(functional_group == "forb") %>% 
  dplyr::select(Block, climate, treatment, functional_group, seed_mass) %>% 
  drop_na() %>% 
  mutate(log_seed_mass = log(seed_mass)) %>% 
  mutate(sqrt_seed_mass = sqrt(seed_mass))

forb_funct_seed_mass <- glmmTMB(data = forb_seed_mass_data, seed_mass ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(forb_funct_seed_mass)
forb_funct_seed_mass <- glmmTMB(data = forb_seed_mass_data, seed_mass ~ climate + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(forb_funct_seed_mass, plot= T) # bad

# log transformation
forb_funct_seed_mass <- glmmTMB(data = forb_seed_mass_data, log_seed_mass ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(forb_funct_seed_mass)
forb_funct_seed_mass <- glmmTMB(data = forb_seed_mass_data, log_seed_mass ~ 1 + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(forb_funct_seed_mass, plot= T) # bad

# square root transformation
forb_funct_seed_mass <- glmmTMB(data = forb_seed_mass_data, sqrt_seed_mass ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
dredge(forb_funct_seed_mass)
forb_funct_seed_mass <- glmmTMB(data = forb_seed_mass_data, sqrt_seed_mass ~ 1 + (1|Block), family = gaussian, na.action = na.fail)
simulateResiduals(forb_funct_seed_mass, plot= T) # bad
```

### Contribution of functinoal group turnover to variance
```{r}
cwm_funct <-  read_csv("~/github/Tejon_Functional_Traits/Datasheets/cwm_traits_updated.csv") %>%
  left_join(other_traits, by = "species_name") %>%
  mutate(weighted_specific_la = leaf_area * Abundance) %>% #multiplying trait values by species abundance
  mutate(weighted_specific_sla = sla * Abundance) %>%
  mutate(weighted_specific_ldmc = ldmc * Abundance) %>%
  mutate(weighted_specific_seed_mass = seed_mass * Abundance) %>%
  mutate(weighted_specific_n = leaf_n * Abundance) %>%
  group_by(climate, treatment, Block, functional_group) %>% #grouping by climate, treatment, and block
  summarise_all(mean, na.rm = TRUE) %>% #finding the mean
  dplyr::select(Block, climate, treatment, functional_group, Abundance, weighted_specific_la, weighted_specific_sla, weighted_specific_ldmc, weighted_specific_seed_mass, weighted_specific_n)

funct_itv_data <-  read_csv("~/github/Tejon_Functional_Traits/Datasheets/cwm_traits_updated.csv") %>%
  left_join(other_traits, by = "species_name") %>% 
  group_by(functional_group) %>%
  summarise_all(mean, na.rm = TRUE) %>% 
  dplyr::select(functional_group, leaf_area, sla, ldmc, seed_mass, leaf_n) %>% 
  rename(leaf_area_fixed = leaf_area, sla_fixed = sla, ldmc_fixed = ldmc, seed_mass_fixed = seed_mass, leaf_n_fixed = leaf_n) %>% 
  left_join(cwm_funct, by = "functional_group") %>% 
  mutate(weighted_fixed_la = leaf_area_fixed * Abundance, 
         weighted_fixed_sla = sla_fixed * Abundance,
         weighted_fixed_ldmc = ldmc_fixed * Abundance,
         weighted_fixed_seed_mass = seed_mass_fixed * Abundance,
         weighted_fixed_leaf_n = leaf_n_fixed * Abundance)
# Leaf Area
shapiro.test(residuals(aov(weighted_specific_la ~ climate * treatment, data = funct_itv_data))) # not normal
shapiro.test(residuals(aov(weighted_fixed_la ~ climate * treatment, data = funct_itv_data))) # not normal
shapiro.test(residuals(aov((weighted_specific_la - weighted_fixed_la) ~ climate * treatment, data = funct_itv_data))) # not normal

shapiro.test(residuals(aov(log(weighted_specific_la) ~ climate * treatment, data = funct_itv_data))) # normal
shapiro.test(residuals(aov(log(weighted_fixed_la) ~ climate * treatment, data = funct_itv_data))) # normal
shapiro.test(residuals(aov(log((weighted_specific_la - weighted_fixed_la)) ~ climate * treatment, data = funct_itv_data))) # normal


la_flex <- trait.flex.anova(~climate*treatment, log(weighted_specific_la), log(weighted_fixed_la), data = funct_itv_data)
print(la_flex)
plot(la_flex, use.percentage=T)

# SLA
shapiro.test(residuals(aov(weighted_specific_sla ~ climate * treatment, data = funct_itv_data))) # normal
shapiro.test(residuals(aov(weighted_fixed_sla ~ climate * treatment, data = funct_itv_data))) # normal
shapiro.test(residuals(aov((weighted_specific_sla - weighted_fixed_sla) ~ climate * treatment, data = funct_itv_data))) # not normal

sla_flex <- trait.flex.anova(~climate*treatment, weighted_specific_sla, weighted_fixed_sla, data = funct_itv_data)
print(sla_flex)
plot(sla_flex, use.percentage=T)

# LDMC
lm_1 <- lm(log(weighted_specific_ldmc) ~ climate * treatment, data = funct_itv_data)
lm_2 <- lm(weighted_fixed_ldmc ~ climate * treatment, data = funct_itv_data)
lm_3 <- lm((weighted_specific_ldmc - weighted_fixed_ldmc) ~ climate * treatment, data = funct_itv_data)
simulateResiduals(lm_1, plot = T) # looks ok
shapiro.test(residuals(lm_1)) # not normal

ldmc_flex_2 <- trait.flex.anova(~climate*treatment, weighted_specific_ldmc, weighted_fixed_ldmc, data = funct_itv_data)
ldmc_flex_3 <- trait.flex.anova(~climate*treatment * functional_group, weighted_specific_ldmc, weighted_fixed_ldmc, data = funct_itv_data)
print(ldmc_flex_2)
print(ldmc_flex_3)
plot(ldmc_flex_2, use.percentage=T)

```

