---
title: "CWM Models"
author: "Maggie Klope"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# loading packages
packages <- c("tidyverse", "ggplot2", "glmmTMB","DHARMa", "MuMIn", "emmeans", "tibble", "multcomp", "car", "ggsignif", "ggeffects", "gt", "effectsize", "lme4")
(lapply(packages, library, character.only = TRUE))

# loading trait data
other_traits <- read_csv("/Users/User_2/github/Tejon_Functional_Traits/Datasheets/seed_mass_leaf_N.csv")

# cwm_int <- read_csv("/Users/User_2/github/Tejon_Functional_Traits/Datasheets/cwm_traits_updated.csv") %>% 
#   left_join(other_traits, by = "species_name")

cwm_traits_adj <-  read_csv("/Users/User_2/github/Tejon_Functional_Traits/Datasheets/cwm_traits_updated.csv") %>% 
  left_join(other_traits, by = "species_name") %>% 
  mutate(weighted_la = leaf_area * Abundance) %>% # multiplying trait values by species abundance
  mutate(weighted_sla = sla * Abundance) %>% 
  mutate(weighted_ldmc = ldmc * Abundance) %>%
  mutate(weighted_seed_mass = seed_mass * Abundance) %>%
  mutate(weighted_n = leaf_n * Abundance) %>% 
  group_by(climate, treatment, Block) %>% # grouping by climate, treatment, and block
  summarise_all(mean, na.rm = TRUE) %>% # finding the mean, skipping over NA values
  dplyr::select(climate, treatment, Block, weighted_la, weighted_sla, weighted_ldmc, weighted_seed_mass, weighted_n)

# adding log transformation for seed mass & leaf n
cwm_traits_adj <- cwm_traits_adj %>% 
  mutate(log_seed_mass = log(weighted_seed_mass)) %>% 
  mutate(log_n = log(weighted_n)) %>% 
  mutate(log_sla = log(weighted_sla)) %>% 
  mutate(log_la = log(weighted_la))

```

- Calculated with 2017 trait data
- Only one block sampled at each climate/treatment, so no blocking effect.

### Questions:

**What is the effect of climate and grazing on community-weighted means?**

**Is there an interaction between climate and grazing?**

### Models:

`glm(LA ~ Climate * Treatment, family = gaussian)`

```{r, include=FALSE}
cwm_bar_data <- cwm_traits_adj %>%
  pivot_longer(cols = weighted_la:weighted_n,
               names_to = "traits",
               values_to = "value")

ggplot(cwm_bar_data, aes(x = climate, y = value)) +
  geom_boxplot(aes(color = treatment)) +
  theme_bw() +
  facet_wrap(~traits, scales = "free", nrow = 3) +
  scale_color_manual(values = c("gray80", "gray50", "gray30"))
  # scale_fill_manual(values = c("#f46d43", "#fee090", "#74add1"))

# ggsave("CWM_barchart.png", path = "/Users/User_2/github//Tejon_Functional_Traits/Figures", width = 9, height = 7)

```

#### a) LA CWM

```{r}
# # climate model:
# LA_CWM_1a <- glmmTMB(data = cwm_traits_adj, weighted_la ~ climate + (1|Block), na.action = na.fail)
# 
# # treatment model:
# LA_CWM_2a <- glmmTMB(data = cwm_traits_adj, weighted_la ~ treatment + (1|Block), na.action = na.fail)
# 
# # interaction model:
# LA_CWM_3a <- gglmmTMB(data = cwm_traits_adj, weighted_la ~ climate * treatment + (1|Block), na.action = na.fail)
# 
# # no interaction
# LA_CWM_4a <- glmmTMB(data = cwm_traits_adj, weighted_la ~ climate + treatment + (1|Block), na.action = na.fail)
# 
# # null model:
# LA_CWM_5a <- glmmTMB(data = cwm_traits_adj, weighted_la ~ 1 + (1|Block), na.action = na.fail)
# 
# AICc(LA_CWM_1a, LA_CWM_2a, LA_CWM_3a,  LA_CWM_4a, LA_CWM_5a) #best model: weighted_la ~ climate * treatment
# 
# # Checking data
# simulateResiduals(LA_CWM_3a, plot = T) # not good

# log transformation
# climate model:
LA_CWM_1 <- glmmTMB(data = cwm_traits_adj, log_la ~ climate + (1|Block), family = gaussian(), na.action = na.fail)

# treatment model:
LA_CWM_2 <- glmmTMB(data = cwm_traits_adj, log_la ~ treatment + (1|Block), family = gaussian(), na.action = na.fail)

# interaction model:
LA_CWM_3 <- glmmTMB(data = cwm_traits_adj, log_la ~ climate * treatment + (1|Block), family = gaussian(), na.action = na.fail)
LA_CWM_3b <- glm(data = cwm_traits_adj, log_la ~ climate * treatment, family = gaussian(), na.action = na.fail)

# no interaction
LA_CWM_4 <- glmmTMB(data = cwm_traits_adj, log_la ~ climate + treatment + (1|Block), family = gaussian(), na.action = na.fail)

# null model:
LA_CWM_5 <- glmmTMB(data = cwm_traits_adj, log_la ~ 1 + (1|Block), family = gaussian(), na.action = na.fail)

AICc(LA_CWM_1, LA_CWM_2, LA_CWM_3, LA_CWM_4, LA_CWM_5) #best model: weighted_la ~ climate * treatment

# Checking data
simulateResiduals(LA_CWM_3, plot = T) # good
shapiro.test(residuals(LA_CWM_3)) # normal

# # significance & comparisons
# library(modEvA)
# r.squaredGLMM(LA_CWM_3)
# RsqGLM(LA_CWM_3b)

LA_CWM_3 
summary(LA_CWM_3)
emmeans(LA_CWM_3, pairwise ~ climate + treatment)

# pairwise comparison plots
plot(emmeans(n_aov, ~ climate + treatment)) 
emmeans(LA_CWM_3, pairwise ~ climate * treatment)

# plot(emmeans(LA_CWM_3, ~ climate * treatment),
#      type = "response",
#      comparisons = TRUE, # If arrows overlap, they are not statistically significant
#      colors = c("black", "black", "blue", "black")) + # color names for estimates, CIs, PIs, and comparison arrows, respectively
#   theme_bw() +  # this is a ggplot so you can customize as normal
#   labs(x = "Estimated marginal mean (LA CWM)", y = "Climate")

```

#### b. SLA CWM

```{r}
# interaction model
SLA_CWM_1  <- glmmTMB(data = cwm_traits_adj, weighted_sla ~ climate * treatment + (1|Block), family = gaussian(), na.action = na.fail) 

# no interaction
SLA_CWM_2  <- glmmTMB(data = cwm_traits_adj, weighted_sla ~ climate + treatment + (1|Block), family = gaussian(), na.action = na.fail) 

# climate model
SLA_CWM_3  <- glmmTMB(data = cwm_traits_adj, weighted_sla ~ climate + (1|Block), family = gaussian(), na.action = na.fail) 

# treatment model
SLA_CWM_4  <- glmmTMB(data = cwm_traits_adj, weighted_sla ~ treatment + (1|Block), family = gaussian(), na.action = na.fail) 

# null model
SLA_CWM_5  <- glmmTMB(data = cwm_traits_adj, weighted_sla ~ 1 + (1|Block), family = gaussian(), na.action = na.fail) 

AICc(SLA_CWM_1, SLA_CWM_2, SLA_CWM_3, SLA_CWM_4, SLA_CWM_5) # best model is interaction model

# Checking data
simulateResiduals(SLA_CWM_1, plot = T) # good
shapiro.test(residuals(SLA_CWM_1)) # normal

# variances are equal
leveneTest(data = cwm_traits_adj, weighted_sla ~ climate * treatment) 

# significance & comparisons
summary(SLA_CWM_1)
anova(SLA_CWM_1)
sla_aov <- aov(SLA_CWM_1)
TukeyHSD(sla_aov)
emmeans(SLA_CWM_1, pairwise ~ climate * treatment)
plot(emmeans(SLA_CWM_1, ~ climate * treatment))

```

#### c. LDMC CWM

```{r}
# interaction model
LDMC_CWM_1 <- glmmTMB(data = cwm_traits_adj, weighted_ldmc ~ climate * treatment + (1|Block), family = gaussian(), na.action = na.fail)

# no interaction model
LDMC_CWM_2 <- glmmTMB(data = cwm_traits_adj, weighted_ldmc ~ climate + treatment + (1|Block), family = gaussian(), na.action = na.fail)

# climate model
LDMC_CWM_3 <- glmmTMB(data = cwm_traits_adj, weighted_ldmc ~ climate + (1|Block), family = gaussian(), na.action = na.fail)

# treatment model
LDMC_CWM_4 <- glmmTMB(data = cwm_traits_adj, weighted_ldmc ~treatment + (1|Block), family = gaussian(), na.action = na.fail)

# null model
LDMC_CWM_5 <- glmmTMB(data = cwm_traits_adj, weighted_ldmc ~ 1 + (1|Block), family = gaussian(), na.action = na.fail)

AICc(LDMC_CWM_1, LDMC_CWM_2, LDMC_CWM_3, LDMC_CWM_4, LDMC_CWM_5) # best fit model is no interaction

simulateResiduals(LDMC_CWM_2, plot= T) #looks good
shapiro.test(residuals(LDMC_CWM_2)) #normal

# variances are equal
leveneTest(data = cwm_traits_adj, weighted_ldmc ~ climate * treatment) 

# significance & comparisons
summary(LDMC_CWM_2)
anova(LDMC_CWM_2)
sla_aov <- aov(LDMC_CWM_2)
TukeyHSD(sla_aov)
emmeans(LDMC_CWM_2, pairwise ~ climate + treatment)
emmeans(LDMC_CWM_2, pairwise ~ climate)
emmeans(LDMC_CWM_2, pairwise ~ treatment)
emmeans(LDMC_CWM_2, pairwise ~ climate + treatment)
plot(emmeans(LDMC_CWM_2, ~ climate + treatment))

```

#### d. Seed mass CWM

```{r}
# 
# # interaction model
# seed_mass_CWM_1 <- glmmTMB(data = cwm_traits_adj, weighted_seed_mass ~ climate * treatment + (1|Block), family = gaussian, na.action = na.fail)
# 
# # no interaction model
# seed_mass_CWM_2 <- glmmTMB(data = cwm_traits_adj, weighted_seed_mass ~ climate + treatment + (1|Block), family = gaussian, na.action = na.fail)
# 
# # climate model
# seed_mass_CWM_3 <- glmmTMB(data = cwm_traits_adj, weighted_seed_mass ~ climate + (1|Block), family = gaussian, na.action = na.fail)
# 
# # treatment model
# seed_mass_CWM_4 <- glmmTMB(data = cwm_traits_adj, weighted_seed_mass ~ treatment + (1|Block), family = gaussian, na.action = na.fail)
# 
# # null model
# seed_mass_CWM_5 <- glmmTMB(data = cwm_traits_adj, weighted_seed_mass ~ 1 + (1|Block), family = gaussian, na.action = na.fail)
# 
# AICc(seed_mass_CWM_1, seed_mass_CWM_2, seed_mass_CWM_3, seed_mass_CWM_4, seed_mass_CWM_5) # lowest AICc is no interacito model
# 
# simulateResiduals(seed_mass_CWM_2, plot= T) # not good
# shapiro.test(residuals(seed_mass_CWM_2)) # not normal


# log transformation

# interaction model
seed_mass_CWM_1 <- glmmTMB(data = cwm_traits_adj, log_seed_mass ~ climate * treatment + (1|Block), family = gaussian(), na.action = na.fail)

# no interaction model
seed_mass_CWM_2 <- glmmTMB(data = cwm_traits_adj, log_seed_mass ~ climate + treatment+ (1|Block), family = gaussian(), na.action = na.fail)

# climate model
seed_mass_CWM_3 <- glmmTMB(data = cwm_traits_adj, log_seed_mass ~ climate+ (1|Block), family = gaussian(), na.action = na.fail)

# treatment model
seed_mass_CWM_4 <- glmmTMB(data = cwm_traits_adj, log_seed_mass ~ treatment+ (1|Block), family = gaussian(), na.action = na.fail)

# null model
seed_mass_CWM_5 <- glmmTMB(data = cwm_traits_adj, log_seed_mass ~ 1+ (1|Block), family = gaussian(), na.action = na.fail)

AICc(seed_mass_CWM_1, seed_mass_CWM_2, seed_mass_CWM_3, seed_mass_CWM_4, seed_mass_CWM_5) # lowest AICc is no interaction model

# residuals are normal
simulateResiduals(seed_mass_CWM_2, plot= T) #looks good
shapiro.test(residuals(seed_mass_CWM_2)) #normal

# variances are equal
leveneTest(data = cwm_traits_adj, log_seed_mass ~ climate * treatment) 

# significance & comparisons
summary(seed_mass_CWM_2)
anova(seed_mass_CWM_2)
seed_aov <- aov(seed_mass_CWM_2)
TukeyHSD(seed_aov)
emmeans(seed_mass_CWM_2, pairwise ~ climate + treatment)
emmeans(seed_mass_CWM_2, pairwise ~ climate)
emmeans(seed_mass_CWM_2, pairwise ~ treatment)
emmeans(seed_mass_CWM_2, pairwise ~ climate + treatment)
plot(emmeans(seed_mass_CWM_2, ~ climate + treatment))


```

#### e. Leaf-N CWM

```{r} 

# interaction model
n_CWM_1 <- glmmTMB(data = cwm_traits_adj, weighted_n ~ climate * treatment + (1|Block), family = gaussian(), na.action = na.fail)

# no interaction model
n_CWM_2 <- glmmTMB(data = cwm_traits_adj, weighted_n ~ climate + treatment + (1|Block), family = gaussian(), na.action = na.fail)

# climate model
n_CWM_3 <- glmmTMB(data = cwm_traits_adj, weighted_n ~ climate + (1|Block), family = gaussian(), na.action = na.fail)

# treatment model
n_CWM_4 <- glmmTMB(data = cwm_traits_adj, weighted_n ~ treatment + (1|Block), family = gaussian(), na.action = na.fail)

# intercept model
n_CWM_5 <- glmmTMB(data = cwm_traits_adj, weighted_n ~ 1 + (1|Block), family = gaussian(), na.action = na.fail)

AICc(n_CWM_1, n_CWM_2, n_CWM_3, n_CWM_4, n_CWM_5) # best is no interaction

# residuals are normal
shapiro.test(residuals(n_CWM_2)) 
qqPlot(residuals(n_CWM_2))

# significance & comparisons
summary(n_CWM_2)
anova(n_CWM_2)
n_aov <- aov(n_CWM_2)
TukeyHSD(n_aov)

emmeans(n_CWM_2, pairwise ~ climate)
emmeans(n_CWM_2, pairwise ~ treatment)
emmeans(n_CWM_2, pairwise ~ climate + treatment)
plot(emmeans(n_CWM_2, ~ climate + treatment))

```

#### f. Best-fit Model Table

```{r}
dredge_LA <- as.data.frame(dredge(LA_CWM_3)) %>%
  arrange(df) %>% 
  mutate(CWM = "Leaf Area")

dredge_SLA <-  as.data.frame(dredge(SLA_CWM_1)) %>%
  arrange(df) %>% 
  mutate(CWM = "Specific Leaf Area")

dredge_LDMC <- as.data.frame(dredge(LDMC_CWM_1)) %>%
    arrange(df) %>% 
  mutate(CWM = "Leaf Dry Matter Content") 

dredge_log_seed_mass <- as.data.frame(dredge(seed_mass_CWM_1)) %>%
    arrange(df) %>% 
  mutate(CWM = "Seed Mass (log)") 

dredge_log_n <- as.data.frame(dredge(n_CWM_1)) %>%
    arrange(df) %>% 
  mutate(CWM = "Leaf Nitrogen Content (log)") 

dredge_table <- dredge_LA %>%
  full_join(dredge_SLA) %>%
  full_join(dredge_LDMC) %>%
  full_join(dredge_log_seed_mass) %>%
  full_join(dredge_log_n) 
# %>%
#   mutate(climate = str_replace(climate, "\\+","x")) %>%
#   mutate(treatment = str_replace(treatment, "\\+","x")) %>%
#   mutate(`climate:treatment` = str_replace(`climate:treatment`, "\\+","x"))

# Trying gt package
# data must be a tibble

# pretty_table <- dredge_table %>% 
#   as_tibble() %>% 
#   gt() %>% 
#   tab_header(
#     title = "CWM Best-Fit Models"
#   ) %>% 
#   tab_spanner(
#     label = "Fixed Effects Terms",
#     columns = vars(climate, treatment, "climate:treatment")
#   ) %>% 
#   fmt_missing(
#     columns = vars(climate, treatment, "climate:treatment"),
#     missing_text = " "
#   ) %>% 
#   tab_source_note(
#     source_note = "x indicates selection of fixed effect term for best-fit model"
#   )

# pretty_table

# gtsave(data = pretty_table, filename = "CWM_Best_Fit_table.png", path = "~/github/Tejon_Functional_Traits/Figures")

```

#### g. AIC Supplement

```{r}
# 
# dredge_LA <- as.data.frame(dredge(LA_CWM)) %>%
#   mutate(CWM = "Leaf Area") %>% 
#   dplyr::select(CWM, climate, treatment, "climate:treatment", AICc)
# 
# dredge_SLA <-  as.data.frame(dredge(SLA_CWM)) %>% 
#   mutate(CWM = "Specific Leaf Area") %>% 
#   dplyr::select(CWM, climate, treatment, "climate:treatment", AICc)
# 
# dredge_LDMC <- as.data.frame(dredge(LDMC_CWM)) %>% 
#   mutate(CWM = "Leaf Dry Matter Content") %>%
#   dplyr::select(CWM, climate, treatment, AICc)
# 
# dredge_log_seed_mass <- as.data.frame(dredge(log_seed_mass)) %>% 
#   mutate(CWM = "Seed Mass (log)") %>%
#   dplyr::select(CWM, climate, treatment, AICc)
# 
# dredge_log_n <- as.data.frame(dredge(log_n_CWM)) %>% 
#   mutate(CWM = "Leaf Nitrogen Content (log)") %>%
#   dplyr::select(CWM, climate, treatment, AICc)
# 
# dredge_table <- dredge_LA %>% 
#   full_join(dredge_SLA) %>% 
#   full_join(dredge_LDMC) %>% 
#   full_join(dredge_log_seed_mass) %>% 
#   full_join(dredge_log_n) %>% 
#   mutate(climate = str_replace(climate, "\\+","x")) %>%
#   mutate(treatment = str_replace(treatment, "\\+","x")) %>% 
#   mutate(`climate:treatment` = str_replace(`climate:treatment`, "\\+","x"))

# dredge_table

# Trying gt package
# data must be a tibble

# cwm_aic_sup <- dredge_table %>% 
#   as_tibble() %>% 
#   dplyr::group_by(CWM) %>%
#   gt() %>% 
#   tab_spanner_delim(delim = ".") %>% 
#   tab_header(
#     title = "CWM Models"
#   ) %>%
#   tab_spanner(
#     label = "Fixed Effects Terms",
#     columns = vars(climate, treatment, "climate:treatment")
#   ) %>%
#   fmt_missing(
#     columns = vars(climate, treatment, "climate:treatment"),
#     missing_text = " "
#   ) %>%
#   tab_source_note(
#     source_note = "x indicates selection of fixed effect term for best-fit model"
#   ) %>% 
#   cols_align(align = "center")

# gtsave(data = cwm_aic_sup, filename = "CWM_AIC_Supplement.png", path = "~/github/Tejon_Functional_Traits/Figures")

```

#### h. testing model summary package

```{r}
library(modelsummary)

modelsummary::datasummary_skim(cwm_traits_adj)

models <- list("SLA" = SLA_CWM_1, 
               "Leaf Area" = LA_CWM_3)

names <- c("climateIntermediate" = "Intermediate Climate", 
           "climateMesic" = "Mesic Climate",
           "treatmentTotal" = "Total Treatment",
           "treatmentPartial" = "Partial Treatment",
           "climateIntermediate × treatmentPartial"= "Intermediate Climate × Partial Treatment")

modelsummary::modelsummary(models, 
                           title = "Community-weighted Means Models",
                           coef_rename = names,
                           stars = TRUE) # won't let me change name of interaction coefficients

```

# trying out Effects package plots
```{r}
library(effects)

treatment_cols <- c("#c7eae5", "#b8e186", "#dfc27d")
treatment_cols <- c("gray30", "gray50", "gray80")
climate_cols <- c("#f46d43", "#fee090", "#74add1")

# leaf area
Anova(LA_CWM_3)
plot(predictorEffect("climate", LA_CWM_3), lines=list(multiline=TRUE, col = treatment_cols), confint=list(style="auto")) 
plot(predictorEffect("treatment", LA_CWM_3), lines=list(multiline=TRUE, col = climate_cols), confint=list(style="auto")) 
plot(predictorEffects(LA_CWM_3, ~ climate * treatment))
plot(predictorEffects(LA_CWM_3, ~ climate * treatment),  lines=list(multiline=TRUE, col = climate_cols), confint=list(style="auto"))

# SLA
Anova(SLA_CWM_1)
plot(predictorEffect("climate", SLA_CWM_1)) 
plot(predictorEffect("treatment", SLA_CWM_1))
# plot(predictorEffects(SLA_CWM_1, ~ climate * treatment))
plot(predictorEffects(SLA_CWM_1, ~ climate * treatment),  lines=list(multiline=TRUE), confint=list(style="auto"))

# LDMC
Anova(LDMC_CWM_2)
plot(predictorEffect("climate", LDMC_CWM_2)) 
plot(predictorEffect("treatment", LDMC_CWM_2))
# plot(predictorEffects(LDMC_CWM_2, ~ climate * treatment))
plot(predictorEffects(LDMC_CWM_2, ~ climate * treatment),  lines=list(multiline=TRUE), confint=list(style="auto"))

plot(predictorEffect("climate", LDMC_CWM_1)) 
plot(predictorEffect("treatment", LDMC_CWM_1))
plot(predictorEffects(LDMC_CWM_1, ~ climate * treatment),  lines=list(multiline=TRUE), confint=list(style="auto"))

# Seed Mass
Anova(seed_mass_CWM_2)
plot(predictorEffect("climate", seed_mass_CWM_2)) 
plot(predictorEffect("treatment", seed_mass_CWM_2))
# plot(predictorEffects(seed_mass_CWM_2, ~ climate * treatment))
plot(predictorEffects(seed_mass_CWM_2, ~ climate * treatment),  lines=list(multiline=TRUE), confint=list(style="auto"))
plot(predictorEffect("climate", seed_mass_CWM_1)) 
plot(predictorEffect("treatment", seed_mass_CWM_1))
plot(predictorEffects(seed_mass_CWM_1, ~ climate * treatment),  lines=list(multiline=TRUE), confint=list(style="auto"))

# Leaf N
plot(predictorEffect("climate", n_CWM_2)) 
plot(predictorEffect("treatment", n_CWM_2))
# plot(predictorEffects(n_CWM_2, ~ climate * treatment))
plot(predictorEffects(n_CWM_2, ~ climate * treatment),  lines=list(multiline=TRUE), confint=list(style="auto"))

```

