---
title: "CWM_Models"
author: "Maggie Klope"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(stats)
library(sjPlot)
library(FD)
library(DHARMa) #model diagnostics
library(glmmTMB) #model fitting
library(MuMIn) #model summaries and comparisons
library(emmeans) #post-hoc analyses
library(gt)
library(tibble)
library(lsmeans)
library(gridExtra)
library(multcomp)
library(car)
# remotes::install_github("const-ae/ggsignif")
library(ggsignif)
library(ggeffects)


other_traits <- read_csv("/Users/User_2/github/Tejon_Functional_Traits/Datasheets/seed_mass_leaf_N.csv")

cwm_traits_adj <-  read_csv("/Users/User_2/github/Tejon_Functional_Traits/Datasheets/cwm_traits_updated.csv") %>% 
  left_join(other_traits, by = "species_name") %>% 
  mutate(weighted_la = leaf_area * Abundance) %>% #multiplying trait values by species abundance
  mutate(weighted_sla = sla * Abundance) %>% 
  mutate(weighted_ldmc = ldmc * Abundance) %>%
  mutate(weighted_seed_mass = seed_mass * Abundance) %>%
  mutate(weighted_n = leaf_n * Abundance) %>%
  group_by(climate, treatment, Block) %>% #grouping by climate, treatment, and block
  summarise_all(mean, na.rm = TRUE) %>% #finding the mean
  dplyr::select(climate, treatment, Block, weighted_la, weighted_sla, weighted_ldmc, weighted_seed_mass, weighted_n)

# log transformation for seed mass & leaf n
cwm_traits_adj <- cwm_traits_adj %>% 
  mutate(log_seed_mass = log(weighted_seed_mass)) %>% 
  mutate(log_n = log(weighted_n))

```

## GLMs for Community-weighted means (CWMs)

- Calculated with 2017 trait data
- again, one value per climate/treatment/block so no blocking effect included

### Models:

**What is the effect of climate and grazing on community-weighted means?**

`lm(LA ~ Climate * Treatment, family = gaussian)`

```{r, include=FALSE}
cwm_bar_data <- cwm_traits_adj %>%
  pivot_longer(cols = weighted_la:weighted_n,
               names_to = "traits",
               values_to = "value")

ggplot(cwm_bar_data, aes(x = climate, y = value)) +
  geom_boxplot(aes(fill = treatment)) +
  theme_bw() +
  facet_wrap(~traits, scales = "free", nrow = 3) +
  scale_fill_manual(values = c("#ffffff", "#d9d9d9", "#969696"))

# ggsave("CWM_barchart.png", path = "~/Users/User_2/github//Tejon_Functional_Traits/Figures", width = 9, height = 7)

```

#### a. LA CWM

- Averaged over treatment, climate is different between Arid-Int and Arid-Mesic
- Averaged over climate, treatment is different between Open-Total and Partial-Total, but not Open-Partial
- Arid Total LA CWM larger than all other plots
- Arid:
    - Arid Total > Arid Open and Arid Partial
    - No difference between Arid Open and Arid Partial
- Intermediate:
    - No difference between herbivore treatments
- Mesic:
    - No difference between herbivore treatments
- Total herbivore treatment:
    - Arid Total larger than Intermediate Total and Mesic Total
    - No difference between Int Total and Mesic Total
- No differences between Open or Partial Treatments across climates


```{r}
# Best fit model:
LA_CWM <- glm(data = cwm_traits_adj, weighted_la ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(LA_CWM) #best model: weighted_la ~ climate * treatment

# Checking data
simulateResiduals(LA_CWM, plot= T) #What is the red asterisk on the model predictions graph?
shapiro.test(residuals(LA_CWM)) #normal

# pairwise comparisons
emmeans(LA_CWM, pairwise ~ climate)
emmeans(LA_CWM, pairwise ~ treatment)
emmeans(LA_CWM, pairwise ~ climate * treatment)

#visualization

# data <- as.data.frame(test$emmeans) %>%
#   mutate(upper_limit = emmean +  SE) %>%
#   mutate(lower_limit = emmean -  SE)
# 
# ggplot(data, aes(x = climate, y = emmean)) +
#   geom_point()+
#   facet_wrap(data$treatment)+
# # geom_ribbon(aes(ymin = data$lower_limit, ymax = data$upper_limit), linetype=2, alpha=0.1)
# # geom_errorbar(aes(ymin = data$lower_limit, ymax = data$upper_limit)
#   geom_pointrange(aes(ymin = data$lower_limit, ymax = data$upper_limit))
#   

# plot(pairs(emmeans(LA_CWM, ~ climate | treatment)), comparisons = TRUE)

# plot(emmeans(LA_CWM, ~ climate * treatment), 
#      type = "response", 
#      comparisons = TRUE, # If arrows overlap, they are not statistically significant
#      colors = c("black", "black", "blue", "black")) + # color names for estimates, CIs, PIs, and comparison arrows, respectively
#   # this is a ggplot so you can customize as normal
#   theme_bw() +   
#   labs(x = "Estimated marginal mean (LA CWM)", y = "Climate")

#Compact Letter Display
la_emm <- emmeans(LA_CWM, ~ climate)
la_cdf <- multcomp::cld(la_emm, alpha = 0.05, Letters = LETTERS)

pretty_table <- la_data_1 %>% 
  as_tibble() %>% 
  gt(rowname_col = "contrast", groupname_col = "functional_group") %>% 
  tab_header(
    title = "Climate by Functional Group") %>% 
  fmt_number("p.value", decimal = 4) %>% 
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = vars(p.value),
      rows = p.value <= 0.05)
  )

plot_model(LA_CWM)

```
##### i. double-checking against ANOVA results
```{r}
# double-checking against anova results
LA_aov <- aov(data = cwm_traits_adj, weighted_la ~ climate * treatment)

dredge(LA_aov)
simulateResiduals(LA_aov, plot = T)
shapiro.test(residuals(LA_aov))

summary(LA_aov)
tukey_LA <- TukeyHSD(LA_aov)
TukeyHSD(LA_aov)
```


#### b. SLA CWM

- Once again, Arid Total larger than almost all other treatments
- Arid trends:
    - Arid Total larger than Arid Open and Arid Partial
    - No significant difference between Arid Total & Partial
- No different between Intermediate herbivore treatments
- No difference between Mesic herbivore treatments
- For Total exclosures, almost follows Arid > Int > Mesic
    - Arid Total > Mesic Total
    - Arid Total > Int total (almost significant, p=0.0546)
    - Int Total > Mesic Total
- Other significant difference:
    - Arid Open > Mesic Open

```{r}
# best fit model
SLA_CWM <- glm(data = cwm_traits_adj, weighted_sla ~ climate * treatment, family = gaussian, na.action = na.fail) 
dredge(SLA_CWM) #best model: weighted_sla ~ climate * treatment

# testing data
simulateResiduals(SLA_CWM, plot= T) #looks good
shapiro.test(residuals(SLA_CWM)) #normal

SLA_sig_pairs <- as.data.frame(pairs(emmeans(SLA_CWM, ~climate * treatment)))%>% 
  filter(p.value <= 0.05)

emmeans(SLA_CWM, pairwise ~ climate)
emmeans(SLA_CWM, pairwise ~ treatment)
emmeans(SLA_CWM, pairwise ~ climate * treatment)


plot(emmeans(SLA_CWM, pairwise ~ treatment * climate), comparisons = TRUE)

sla_emm <- emmeans(SLA_CWM, ~ climate)
multcomp::cld(sla_emm, alpha = 0.05, Letters = LETTERS)

```

#### c. LDMC CWM

- Same trend observed between all climates
- Same trend observed between all treatments
- Arid:
    - Arid-Partial < Arid-Total
    - No difference between Partial and Open
    - No difference between Total and Open
- Int:
   - Int-Partial < Int-Total
   - No difference between Partial and Open
   - No difference between Total and Open
- Mesic: 
    - Mesic-Partial < Mesic-Total
    - No difference between Partial and Open
    - No difference between Total and Open
- Open treatment:
    - Int-Open > Arid-Open
    - Int-Open > Mesic-Open
    - No difference between Arid-Open and Mesic-Open
- Partial Treatment:
    - Int-Partial > Arid-Partial
    - Int-Partial > Mesic-Partial
    - No difference between Arid-Partial and Mesic-Partial
- Total Treatment:
    - Int-Total > Arid-Total
    - Int-Total > Mesic-Total
    - No difference between Arid-Total and Mesic-Total

```{r}
LDMC_CWM <- glm(data = cwm_traits_adj, weighted_ldmc ~ climate * treatment, family = gaussian, na.action = na.fail) 
dredge(LDMC_CWM) #best model: weighted_ldmc ~ climate + treatment
LDMC_CWM <- glm(data = cwm_traits_adj, weighted_ldmc ~ climate + treatment, family = gaussian, na.action = na.fail) 

simulateResiduals(LDMC_CWM, plot= T) #looks good
shapiro.test(residuals(LDMC_CWM)) #normal

LDMC_sig_pairs <- as.data.frame(pairs(emmeans(LDMC_CWM, ~climate + treatment))) %>% 
  filter(p.value <= 0.05)

emmeans(LDMC_CWM, pairwise ~ climate)
emmeans(LDMC_CWM, pairwise ~ treatment)
emmeans(LDMC_CWM, pairwise ~ climate + treatment)

plot(emmeans(LDMC_CWM, pairwise ~ treatment + climate), comparisons = TRUE)
multcomp::cld(emmeans(LDMC_CWM, ~ treatment), alpha = 0.05, Letters = LETTERS)

```

#### d. Seed mass CWM

- same trend observed across climates
- same trend observed across herbivore treatments
-Arid
    - Arid-Total > Arid-Open
    - No difference between Arid-Open and Arid-Partial
    - No difference between Arid-Partial and Arid-Total
- Int
    -Int-Total > Int-Open
    - No difference between Int-Open and Int-Partial
    - No difference between Int-Partial and Int-Total
- Mesic
    -Mesic-Total > Mesic-Open
    - No difference between Mesic-Open and Mesic-Partial
    - No difference between Mesic-Partial and Mesic-Total
- Open:
  - Int Open > Mesic-Open
  - No difference between Arid and Mesic
- Partial:
    - Int-Partial > Mesic-Partial
    - No difference between Arid and Mesic
- Total:
    - Int-Total > Mesic-Total
    - No difference between Arid and Mesic

```{r}
# seed_mass_CWM <- glm(data = cwm_traits_adj, weighted_seed_mass ~ climate * treatment, family = gaussian, na.action = na.fail)
# dredge(seed_mass_CWM) #best model: weighted_seed_mass ~ cliamte + treatment
# seed_mass_CWM <- glm(data = cwm_traits_adj, weighted_seed_mass ~ climate + treatment, family = gaussian, na.action = na.fail)

# simulateResiduals(seed_mass_CWM, plot= T) #model predictions look a little wonky, but it says it's good.  I'm also getting something saying that "outer Newton did not converge fully?
# shapiro.test(residuals(seed_mass_CWM)) # not normal

# log transformation
log_seed_mass <- glm(data = cwm_traits_adj, log_seed_mass ~ climate * treatment, family = gaussian, na.action = na.fail)
dredge(log_seed_mass) #best model: weighted_seed_mass ~ cliamte + treatment
log_seed_mass <- glm(data = cwm_traits_adj, log_seed_mass ~ climate + treatment, family = gaussian, na.action = na.fail)

simulateResiduals(log_seed_mass, plot= T) #looks ok
shapiro.test(residuals(log_seed_mass)) #normal

#pairwise comparisons
seed_sig_pairs <-  as.data.frame(pairs(emmeans(log_seed_mass, ~ climate + treatment))) %>% 
  filter(p.value <= 0.05)

emmeans(log_seed_mass, pairwise ~ climate)
emmeans(log_seed_mass, pairwise ~ treatment)
emmeans(log_seed_mass, pairwise ~ climate + treatment)

plot(emmeans(log_seed_mass, pairwise ~ treatment + climate))
multcomp::cld(emmeans(log_seed_mass, ~ treatment), alpha = 0.05, Letters = LETTERS)

```

#### e. Leaf-N CWM

- No difference between any of the different herbivore treatments within climates
- Same pattern observed between treatments at different climates

- Arid:
    - No difference between treatments at Arid
- Int:
     - No difference between  treatments at Int
- Mesic:
    - No difference between treatments at Mesic
- Open:
    - Arid-Open > Mesic-Open
    - Int-Open > Mesic-Open
- Partial:
    - Arid-Partial > Mesic-Partial
    - Int-Partial > Mesic-Partial
- Total:
    - Arid-Total > Mesic-Total
    - Int-Total > Mesic-Total

```{r} 
# leaf_n_CWM <- glm(data = cwm_traits_adj, weighted_n ~ climate * treatment, family = gaussian, na.action = na.fail) 
# dredge(leaf_n_CWM) #best model: weighted_n ~ climate + treatment
# leaf_n_CWM <- glm(data = cwm_traits_adj, weighted_n ~ climate + treatment, family = gaussian, na.action = na.fail) 
# 
# simulateResiduals(leaf_n_CWM, plot= T) #looks bad
# shapiro.test(residuals(leaf_n_CWM)) #not normal

#log transformation
log_n_CWM <- glm(data = cwm_traits_adj, log_n ~ climate * treatment, family = gaussian, na.action = na.fail) 
dredge(log_n_CWM) #get: Fixed terms are "cond((Int))" and "disp((Int))"
log_n_CWM <- glm(data = cwm_traits_adj, log_n ~ climate + treatment, family = gaussian, na.action = na.fail) 

simulateResiduals(log_n_CWM, plot= T) #doesn't look very good
shapiro.test(residuals(log_n_CWM)) #p = 0.05924

# Model summary
emmeans(log_n_CWM, ~climate + treatment)
LNC_pairs <-  as.data.frame(pairs(emmeans(log_n_CWM, ~ climate + treatment)))
LNC_sig_pairs <- LNC_pairs %>% 
  filter(p.value <= 0.05)

emmeans(log_n_CWM, pairwise ~ climate + treatment)

# log_n_contrasts <- as.data.frame(summary(emmeans(log_n_CWM, pairwise ~ climate  treatment))) %>% 
#   dplyr::select(contrasts.contrast, contrasts.treatment, contrasts.estimate, contrasts.p.value) %>% 
#   mutate(significance = ifelse(contrasts.p.value < 0.05, "*", " ")) %>% 
#   rename(Climates = "contrasts.contrast", Treatment = contrasts.treatment, Estimate = contrasts.estimate, "p-value" = contrasts.p.value)

# write.csv(log_n_contrasts, file = "~/github/Tejon_Functional_Traits/Datasheets/log_n_contrasts.", row.names = FALSE)

plot(emmeans(log_n_CWM, pairwise ~ treatment + climate))
multcomp::cld(emmeans(log_n_CWM, ~ treatment), alpha = 0.05, Letters = LETTERS)

summary(lm(data = cwm_traits_adj, log_n ~ climate + treatment))
```

#### f. Best-fit Model Table

```{r}
dredge_LA <- as.data.frame(dredge(LA_CWM)) %>%
  filter(AICc == min(AICc)) %>% 
  mutate(CWM = "Leaf Area") %>% 
  dplyr::select(CWM, climate, treatment, "climate:treatment")

dredge_SLA <-  as.data.frame(dredge(SLA_CWM)) %>% 
  filter(AICc == min(AICc)) %>% 
  mutate(CWM = "Specific Leaf Area") %>% 
  dplyr::select(CWM, climate, treatment, "climate:treatment")

dredge_LDMC <- as.data.frame(dredge(LDMC_CWM)) %>% 
  filter(AICc == min(AICc)) %>% 
  mutate(CWM = "Leaf Dry Matter Content") %>%
  dplyr::select(CWM, climate, treatment)

dredge_log_seed_mass <- as.data.frame(dredge(log_seed_mass)) %>% 
  filter(AICc == min(AICc)) %>% 
  mutate(CWM = "Seed Mass (log)") %>%
  dplyr::select(CWM, climate, treatment)

dredge_log_n <- as.data.frame(dredge(log_n_CWM)) %>% 
  filter(AICc == min(AICc)) %>% 
  mutate(CWM = "Leaf Nitrogen Content (log)") %>%
  dplyr::select(CWM, climate, treatment)

dredge_table <- dredge_LA %>% 
  full_join(dredge_SLA) %>% 
  full_join(dredge_LDMC) %>% 
  full_join(dredge_log_seed_mass) %>% 
  full_join(dredge_log_n) %>% 
  mutate(climate = str_replace(climate, "\\+","x")) %>%
  mutate(treatment = str_replace(treatment, "\\+","x")) %>% 
  mutate(`climate:treatment` = str_replace(`climate:treatment`, "\\+","x"))

# Trying gt package
# data must be a tibble

pretty_table <- dredge_table %>% 
  as_tibble() %>% 
  gt() %>% 
  tab_header(
    title = "CWM Best-Fit Models"
  ) %>% 
  tab_spanner(
    label = "Fixed Effects Terms",
    columns = vars(climate, treatment, "climate:treatment")
  ) %>% 
  fmt_missing(
    columns = vars(climate, treatment, "climate:treatment"),
    missing_text = " "
  ) %>% 
  tab_source_note(
    source_note = "x indicates selection of fixed effect term for best-fit model"
  )

# pretty_table

# gtsave(data = pretty_table, filename = "CWM_Best_Fit_table.png", path = "~/github/Tejon_Functional_Traits/Figures")

```

#### g. AIC Supplement

```{r}

dredge_LA <- as.data.frame(dredge(LA_CWM)) %>%
  mutate(CWM = "Leaf Area") %>% 
  dplyr::select(CWM, climate, treatment, "climate:treatment", AICc)

dredge_SLA <-  as.data.frame(dredge(SLA_CWM)) %>% 
  mutate(CWM = "Specific Leaf Area") %>% 
  dplyr::select(CWM, climate, treatment, "climate:treatment", AICc)

dredge_LDMC <- as.data.frame(dredge(LDMC_CWM)) %>% 
  mutate(CWM = "Leaf Dry Matter Content") %>%
  dplyr::select(CWM, climate, treatment, AICc)

dredge_log_seed_mass <- as.data.frame(dredge(log_seed_mass)) %>% 
  mutate(CWM = "Seed Mass (log)") %>%
  dplyr::select(CWM, climate, treatment, AICc)

dredge_log_n <- as.data.frame(dredge(log_n_CWM)) %>% 
  mutate(CWM = "Leaf Nitrogen Content (log)") %>%
  dplyr::select(CWM, climate, treatment, AICc)

dredge_table <- dredge_LA %>% 
  full_join(dredge_SLA) %>% 
  full_join(dredge_LDMC) %>% 
  full_join(dredge_log_seed_mass) %>% 
  full_join(dredge_log_n) %>% 
  mutate(climate = str_replace(climate, "\\+","x")) %>%
  mutate(treatment = str_replace(treatment, "\\+","x")) %>% 
  mutate(`climate:treatment` = str_replace(`climate:treatment`, "\\+","x"))

# dredge_table

# Trying gt package
# data must be a tibble

cwm_aic_sup <- dredge_table %>% 
  as_tibble() %>% 
  dplyr::group_by(CWM) %>%
  gt() %>% 
  tab_spanner_delim(delim = ".") %>% 
  tab_header(
    title = "CWM Models"
  ) %>%
  tab_spanner(
    label = "Fixed Effects Terms",
    columns = vars(climate, treatment, "climate:treatment")
  ) %>%
  fmt_missing(
    columns = vars(climate, treatment, "climate:treatment"),
    missing_text = " "
  ) %>%
  tab_source_note(
    source_note = "x indicates selection of fixed effect term for best-fit model"
  ) %>% 
  cols_align(align = "center")

# gtsave(data = cwm_aic_sup, filename = "CWM_AIC_Supplement.png", path = "~/github/Tejon_Functional_Traits/Figures")

```

#### h. testing model summary package

```{r}
library(modelsummary)

modelsummary::datasummary_skim(cwm_traits_adj)

models <- list("SLA" = SLA_CWM, 
               "Leaf Area" = LA_CWM)

names <- c("climateIntermediate" = "Intermediate Climate", 
           "climateMesic" = "Mesic Climate",
           "treatmentTotal" = "Total Treatment",
           "treatmentPartial" = "Partial Treatment",
           "climateIntermediate × treatmentPartial"= "Intermediate Climate × Partial Treatment")

modelsummary::modelsummary(models, 
                           title = "Community-weighted Means Models",
                           coef_rename = names,
                           stars = TRUE) # won't let me change name of interaction coefficients

```

